### 2020-04-16 Paper/EEET2493_labreport_template.tex
Added LaTeX template for Paper

\documentclass[journal]{IEEEtran}

% *** CITATION PACKAGES ***
\usepackage[style=ieee]{biblatex} 
\bibliography{random_walk.bib}    %your file created using JabRef

% *** MATH PACKAGES ***
\usepackage{amsmath}

% *** PDF, URL AND HYPERLINK PACKAGES ***
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}  %needed to include png, eps figures
\usepackage{float}  % used to fix location of images i.e.\begin{figure}[H]

\begin{document}

% paper title
\title{Using Random Walk Simulations to Calculate Ground State Energies in Quantum Physics}

% author names 
\author{Sai Pandian, ID: 29899923}% <-this % stops a space

% The report headers
\markboth{PHYS6017 Computer Techniques in Physics Report 1, April 2020}
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Provide a summary of the session. What was done, 
what measurements were taken, brief methods, what calculations, brief conclusion.  The Abstract should be approximately 250 words or fewer, italicized, in 10-point Times (or Times Roman.) Please leave two spaces between the Abstract and the heading of your first section.
It should briefly summarize the essence of the paper and address the following areas without using specific subsection titles. Objective: Briefly state the problem or issue addressed, in language accessible to a general scientific audience. Technology or Method: Briefly summarize the technological innovation or method used to address the problem. Results: Provide a brief summary of the results and findings. Conclusions: Give brief concluding remarks on your outcomes. Detailed discussion of these aspects should be provided in the main body of the paper.
\end{abstract}

\begin{IEEEkeywords}
keywords, temperature, xxxx equation, etc.
\end{IEEEkeywords}

\section{Introduction}
% Here we have the typical use of a "W" for an initial drop letter
% and "RITE" in caps to complete the first word.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

\IEEEPARstart{S}{ample} Text

\section{Theoretical Background}

Sample Text

\section{Method}

\begin{table}[!ht] %[H]
\centering
\label{table:Exps}
\begin{tabular}{ll}
Student &  Max Temperature \\ \hline
aabbbccc &  $35^{\circ}$   \\
eeeddd &   $54^{\circ}$ \\
eeeddd &   $54^{\circ}$ \\
\end{tabular}
\caption{Temperature measurements performed for session 1.}
\end{table}

\begin{figure}[H]%[!ht]
\begin {center}
\includegraphics[width=0.45\textwidth]{images/ecg.png}
\caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
\label{fig:ecg}
\end {center}
\end{figure}

\section{Results and Discussion}

Sample Text

\section{Conclusions}

Sample Text

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
\section{Hand calculations (or name your title for appendix subtitle)}

Sample Text

\section*{Acknowledgment}
The authors would like to thank...

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

%use following command to generate the list of cited references

\printbibliography

% that's all folks
\end{document}

### 2020-04-16 plotcpp.py
Plots can now be saved and removed unncessry function

@@ -49,6 +49,7 @@ def exp_plot(data, show=True, skip=0, start=1):
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.show()
+        plt.savefig("./Paper/images/exp_plot.pdf")
     return popt[1]
 
 
@@ -80,6 +81,7 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.show()
+        plt.savefig("./Paper/images/cum_exp_plot.pdf")
 
     return popt[1]
 
@@ -108,6 +110,7 @@ def line_plot(data, show=True, skip=0, start=1):
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.show()
+        plt.savefig("./Paper/images/line_plot.pdf")
     return popt[1]
 
 
@@ -136,29 +139,8 @@ def cum_line_plot(data, show=True, skip=0, start=1):
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.show()
+        plt.savefig("./Paper/images/cum_line_plot.pdf")
     return popt[1]
-
-
-def find_remove(data, maxNumber, show=True):
-    N = maxNumber
-    val = []
-    x = range(N)
-    for num in x:
-        fit = cum_line_plot(data, show=False, skip=num, start=boundary)
-        val.append(fit)
-    if show:
-        plt.plot(x, val)
-        plt.show()
-    x = np.arange(0, N, 1)
-    dx = x[1] - x[0]
-    y = val
-    dydx = np.gradient(y, dx)
-
-    if show:
-        plt.plot(x[:-1], dydx[:-1], ls="", marker='o')
-        popt, _ = curve_fit(exp_curve, x, dydx)
-        plt.plot(x, exp_curve(x, *popt))
-        plt.show()
 
 
 if __name__ == "__main__":

### 2020-04-17 lattice.cpp
Added Circular potential option
Can now work with cirular potential. This is extensible to multiple dimensions

@@ -6,6 +6,7 @@
 #include <fstream>
 #include <ctime>
 #include <string>
+#include <cmath>
 
 using namespace std;
 
@@ -126,6 +127,18 @@ public:
 				return false;
 			}
 
+			if(potential == "circle"){
+				double tmp = 0;
+				for(int i=0; i<coordinates.size(); i++){
+					tmp = tmp + (coordinates[i] * coordinates[i]);
+				}
+				tmp = sqrt(tmp);
+				if(!(tmp < boundary)){
+					return true;
+				}
+				return false;
+			}
+			
 			else{
 				return false;
 			}

### 2020-04-17 plotcpp.py
Fixed error where plot is cleared before figure is saved

@@ -48,8 +48,8 @@ def exp_plot(data, show=True, skip=0, start=1):
         plt.ylabel('Probability')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        plt.show()
         plt.savefig("./Paper/images/exp_plot.pdf")
+        plt.show()
     return popt[1]
 
 
@@ -80,8 +80,8 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
         plt.ylabel('Probability')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        plt.show()
         plt.savefig("./Paper/images/cum_exp_plot.pdf")
+        plt.show()
 
     return popt[1]
 
@@ -109,8 +109,8 @@ def line_plot(data, show=True, skip=0, start=1):
         plt.ylabel('log(Probability)')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        plt.show()
         plt.savefig("./Paper/images/line_plot.pdf")
+        plt.show()
     return popt[1]
 
 
@@ -138,8 +138,8 @@ def cum_line_plot(data, show=True, skip=0, start=1):
         plt.ylabel('log(Probability)')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        plt.show()
         plt.savefig("./Paper/images/cum_line_plot.pdf")
+        plt.show()
     return popt[1]
 
 
@@ -147,7 +147,7 @@ if __name__ == "__main__":
 
     dimen = 1
     iteration = 1000000
-    maxSteps = 0
+    maxSteps = 2000
     potential = "square"
     boundary = 20
     prob = 0.1

### 2020-04-17 cartoon.py
Script to create random walk cartoon
The cartoon better demonstrates how the random walk works

@@ -1,0 +1,18 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import random
+
+length = 20
+x = np.linspace(0, length, length+1)
+y = [0]
+
+for i in range(length):
+    y.append(y[i] + random.choice([-1, 1]))
+
+plt.rc("text", usetex=True)
+plt.rc("font", family="Serif")
+plt.plot(x, y, marker='o', markersize=20)
+plt.xlabel("Step Number")
+plt.ylabel("Position")
+plt.savefig("./Paper/images/cartoon.pdf")
+plt.show()

### 2020-04-17 Paper/main.tex
Renamed files

\documentclass[journal]{IEEEtran}

% *** CITATION PACKAGES ***
\usepackage[style=ieee]{biblatex} 
\bibliography{random_walk.bib}    %your file created using JabRef

% *** MATH PACKAGES ***
\usepackage{amsmath}

% *** PDF, URL AND HYPERLINK PACKAGES ***
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}  %needed to include png, eps figures
\usepackage{float}  % used to fix location of images i.e.\begin{figure}[H]

% *** MY PACKAGES ***
\usepackage{todonotes}

\begin{document}

% paper title
\title{Using Random Walk Simulations to Calculate Ground State Energies in Quantum Physics}

% author names 
\author{Sai Pandian, ID: 29899923}% <-this % stops a space

% The report headers
\markboth{PHYS6017 Computer Techniques in Physics Report 1, April 2020}
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Provide a summary of the session. What was done, what measurements were taken,
brief methods, what calculations, brief conclusion.  The Abstract should be
approximately 250 words or fewer, italicized, in 10-point Times (or Times
Roman.) Please leave two spaces between the Abstract and the heading of your
first section.  It should briefly summarize the essence of the paper and address
the following areas without using specific subsection titles. Objective: Briefly
state the problem or issue addressed, in language accessible to a general
scientific audience. Technology or Method: Briefly summarize the technological
innovation or method used to address the problem. Results: Provide a brief
summary of the results and findings. Conclusions: Give brief concluding remarks
on your outcomes. Detailed discussion of these aspects should be provided in the
main body of the paper.
\end{abstract}

\begin{IEEEkeywords}
keywords, temperature, xxxx equation, etc.
\end{IEEEkeywords}

\section{Introduction}
% Here we have the typical use of a "W" for an initial drop letter
% and "RITE" in caps to complete the first word.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

\IEEEPARstart{R}{andom} walks are a simple model of motion in which a path is
described as a succession of steps with each step being in a random direction on
some vector space. Random walks are useful in modelling many physical processes
that are perceived as having a pseudo-random mechanism \todo{cite}. Their
applications range from Biology to the Stock Market. This paper aims to explore
how Random Walk Simulations can be implemented to calculate the ground state
energies of different quantum systems. \todo{more}

\section{Theoretical Background}

Random walks work descibe motion as a series of steps, with the direction of
each step being random. Figure \ref{fig:cartoon} demonstrates this concept by
considering a one-dimensional line. On this line, the ``walker'' starts at the
origin, and walks a total of 20 steps. The walker at each step has a equal
chance of stepping forwards, or stepping backwards.

\begin{figure}%[H]%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/cartoon.pdf}
    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
    \label{fig:cartoon}
  \end{center}
\end{figure}

As can be seen from the figure, it is not uncommon for the average position of
the walker to be away from the origin once the walk has concluded. This is
because the position of the walker at any step is dependent only on the position
at the previous step. If the walker happens to take a number of steps in the
same direction, it is highly unlikely for the walker to take an equal number of
steps in the opposite direction, in order to return to the origin. Thus, in such
a case, it is likely that the walker will conclude the walk in a position away
from the origin.

In this example, the walker had an equal likelihood of stepping forward or
backwards, but we can bias in one way if we want to model a particular
phenomenon. The walk is also easily extensible to multiple dimensions, as for
each extra dimension, one extra random number must be drawn. This gives a linear
increase in time-complexity, which is convenient for long computations.

Random Walk simulations can be applied to calculate the ground state energies of
Quantum Systems by solving the Schr\"{o}dinger equation. Consider a
one-dimensional simple lattice system. A walker can start at a position labelled
the origin, and then proceed in a random walk. The random walk concludes after a
certain number of steps or if the walker ``dies'' on a particular step. The
probability that the walker will die is dependent on a defined potential at that
point. For example, in an infinite square well system, the potential is 0 within
a well, and infinite outside the well. So the walker will have no chance of
dying whilst inside the well, but will die if they step outside.

Let us define $p(j,n)$ as the probability that the walker will be at position
$j$ after $n$ steps and $a(j)$ as the probability that the walker will die at
position $j$. If we say:

\begin{equation}
  p(j,n) = q(j) exp(-\lambda n)
  \nonumber
\end{equation}
where $q(j)$ is an arbitrary function and $\lambda$ is the rate of death, then:
\begin{equation}
  -\frac{1}{2} \frac{d^2q(j)}{dj^2} + a(j)q(j) = \lambda q(j)
  \nonumber
\end{equation}

\section{Results and Discussion}

Sample Text

\begin{figure}[H]%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/exp_plot.pdf}
    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
    \label{fig:exp_plot}
  \end{center}
\end{figure}

\begin{figure}[H]%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/line_plot.pdf}
    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
    \label{fig:line_plot}
  \end{center}
\end{figure}

\begin{figure}[H]%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/cum_exp_plot.pdf}
    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
    \label{fig:cum_exp_plot}
  \end{center}
\end{figure}

\begin{figure}[H]%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/cum_line_plot.pdf}
    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
    \label{fig:cum_line_plot}
  \end{center}
\end{figure}

\begin{figure}[H]%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/cum_line_plot_cutoff.pdf}
    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
    \label{fig:cum_line_cutoff_plot}
  \end{center}
\end{figure}

\section{Conclusions}

Sample Text

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
\section{Random Walk Schr\"{o}dinger Equation Derivation}
Let us denote the probability that the walker is at position $j$ after $n$ steps
as $p(j,n)$ and the probabilty that the walker will die at position $j$ as
$a(j)$. We will denote the position-step number coordinates as $[j, n]$. Thus,
for a walker to have coordinates $[j, n+1]$, in the previous step, they must have
had coordinates $[j \pm 1, n]$. So we can say:

\begin{equation}
  \label{eq:probability}
  p(j, n+1) =  \frac{1}{2}(1-a(j))(p(j-1,n) + p(j+1,n))
\end{equation}

If $a(j)$ is small and $n$ is large, then we can say $p(j, n)$ is a continuous
function and we can use Taylor expansion to expand each of $p(j+1, n)$,
$p(j-1,n)$, and $p(j, n+1)$:

\begin{equation}
  p(j+1, n) = p(j,n) + \frac{\partial p}{\partial j} + \frac{1}{2}
  \frac{\partial^2 p}{\partial j^2} + ...
  \nonumber
\end{equation}
\begin{equation}
  p(j-1, n) = p(j,n) - \frac{\partial p}{\partial j} + \frac{1}{2}
  \frac{\partial^2 p}{+\partial j^2} + ...
  \nonumber
\end{equation}
\begin{equation}
  p(j, n+1) = p(j, n) + \frac{\partial p}{\partial n} + ...
  \nonumber
\end{equation}

We can now substitute these expansions into Equation \ref{eq:probability}, we
find:

\begin{equation}
  p(j, n) + \frac{\partial p}{\partial n} = (1-a(j))\Big(p +
  \frac{1}{2}\frac{\partial^2 p}{\partial j^2}\Big)
  \nonumber
\end{equation}

But the probability of death $a(j)$ and the second derivative are so small, that
their product is neglected. We also let $p(j,n) = q(j) exp(-\lambda n)$ so that:

\begin{equation}
  item
  \nonumber
\end{equation}

% use section* for acknowledgment
\section*{Acknowledgment}
The authors would like to thank...

\printbibliography

% that's all folks
\end{document}

### 2020-04-17 Paper/main.tex
Completed theoretical Background section

@@
   -\frac{1}{2} \frac{d^2q(j)}{dj^2} + a(j)q(j) = \lambda q(j)
-  \nonumber
+  \label{eq:randomwave}
 \end{equation}
+
+The full derivation is taken from \todo{cite} and is shown in Appendix
+\ref{appendix:derivation}.
+
+Notice that Equation \ref{eq:randomwave} is in the form of a wave equation,
+specifically the Schr\"{o}dinger equation:
+\begin{equation}
+  \label{eq:schrodinger}
+  \frac{-\hbar^2}{2m}\frac{d^2 \psi}{dr^2} + V(r)\psi(r) = E\psi(r)
+\end{equation}
+Comparing Equation \ref{eq:randomwave} and Equation \ref{eq:schrodinger}, we can
+see that the probability of death $a(j)$ is analogous to the potential $V(r)$,
+and the rate of death $\lambda$ is analogous to the Energy $E$. Thus, by running
+the simulation for a particulat potential (i.e. rate of death), one can
+determine the ground state energy of a system by calculating the rate of
+death. This is the technique employed in this paper.
 
@@
 \section{Random Walk Schr\"{o}dinger Equation Derivation}
+\label{appendix:derivation}
 Let us denote the probability that the walker is at position $j$ after $n$ steps
@@
 \begin{equation}
-  item
+  -\frac{1}{2} \frac{d^2q(j)}{dj^2} + a(j)q(j) = \lambda q(j)
   \nonumber
@@
 
-% use section* for acknowledgment
-\section*{Acknowledgment}
-The authors would like to thank...
-
 \printbibliography
 
-% that's all folks
 \end{document}

### 2020-04-17 plotcpp.py
Changed axis labels

@@ -45,7 +45,7 @@ def exp_plot(data, show=True, skip=0, start=1):
     if show:
         # plt.plot(x, exp_curve(x, *popt), c='r', label="Fitted Curve")
 
-        plt.ylabel('Probability')
+        plt.ylabel('Probability of Death')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.savefig("./Paper/images/exp_plot.pdf")
@@ -77,7 +77,7 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
         plt.bar(x, cum_y, width=2, align='center')
         plt.plot(x, exp_curve(x, *popt), c='r', label="Fitted Curve")
 
-        plt.ylabel('Probability')
+        plt.ylabel('Probability of Survival')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.savefig("./Paper/images/cum_exp_plot.pdf")
@@ -106,7 +106,7 @@ def line_plot(data, show=True, skip=0, start=1):
         plt.plot(x, y, marker='.', ls=' ')
         # plt.plot(x, exp_curve(x, *popt), c='r', label="Fitted Curve")
 
-        plt.ylabel('log(Probability)')
+        plt.ylabel('log(Probability of Death)')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.savefig("./Paper/images/line_plot.pdf")
@@ -135,7 +135,7 @@ def cum_line_plot(data, show=True, skip=0, start=1):
         plt.plot(x, cum_y, marker='.', ls=' ')
         plt.plot(x, exp_curve(x, *popt), c='r', label="Fitted Curve")
 
-        plt.ylabel('log(Probability)')
+        plt.ylabel('log(Probability of Survival)')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.savefig("./Paper/images/cum_line_plot.pdf")

### 2020-04-17 Paper/main.tex
Finished draft of Theoretical Background and Method section

@@
 \begin{abstract}
-Provide a summary of the session. What was done, what measurements were taken,
-brief methods, what calculations, brief conclusion.  The Abstract should be
-approximately 250 words or fewer, italicized, in 10-point Times (or Times
-Roman.) Please leave two spaces between the Abstract and the heading of your
-first section.  It should briefly summarize the essence of the paper and address
-the following areas without using specific subsection titles. Objective: Briefly
-state the problem or issue addressed, in language accessible to a general
-scientific audience. Technology or Method: Briefly summarize the technological
-innovation or method used to address the problem. Results: Provide a brief
-summary of the results and findings. Conclusions: Give brief concluding remarks
-on your outcomes. Detailed discussion of these aspects should be provided in the
-main body of the paper.
+% Provide a summary of the session. What was done, what measurements were taken,
+% brief methods, what calculations, brief conclusion.  The Abstract should be
+% approximately 250 words or fewer, italicized, in 10-point Times (or Times
+% Roman.) Please leave two spaces between the Abstract and the heading of your
+% first section.  It should briefly summarize the essence of the paper and address
+% the following areas without using specific subsection titles. Objective: Briefly
+% state the problem or issue addressed, in language accessible to a general
+% scientific audience. Technology or Method: Briefly summarize the technological
+% innovation or method used to address the problem. Results: Provide a brief
+% summary of the results and findings. Conclusions: Give brief concluding remarks
+% on your outcomes. Detailed discussion of these aspects should be provided in the
+% main body of the paper.
 \end{abstract}
@@
 \section{Theoretical Background}
+\label{sec:TheoreticalBackground}
 
@@
 \begin{equation}
-  p(j,n) = q(j) exp(-\lambda n)
-  \nonumber
+  p(j,n) = q(j) \exp(-\lambda n)
+  \label{eq:firsteq}
 \end{equation}
@@
 Comparing Equation \ref{eq:randomwave} and Equation \ref{eq:schrodinger}, we can
-see that the probability of death $a(j)$ is analogous to the potential $V(r)$,
-and the rate of death $\lambda$ is analogous to the Energy $E$. Thus, by running
-the simulation for a particulat potential (i.e. rate of death), one can
+see that the probability of death $a(j)$ is related to the potential $V(r)$,
+and the rate of death $\lambda$ is related to the Energy $E$. Thus, by running
+the simulation for a particular potential (i.e. rate of death), one can
 determine the ground state energy of a system by calculating the rate of
 death. This is the technique employed in this paper.
+
+\section{Method}
+
+The Random Walk is implemented computationally \todo{cite} and is extensible
+to multiple dimensions. For a $N$-dimensional lattice, at each point there are
+$2N$ possible directions for the walker to move. So a direction is selected
+randomly using a Mersenne Twister pseudorandom number generator (pRNG). This algorithm
+was chosen as it is a very fast implementation of a pRNG \todo{cite} and it
+passes many statistical randomness tests \todo{cite}, having a very large
+period of $2^{19937-1}$.
+
+The random walk ends when a walker dies, with a
+specifically chosen $a(j)$. Initially, the $a(j)$ is chosen to be that of an
+infinite square well, that is:
+\begin{equation}
+  \label{eq:squarewell}
+    a(j) =
+    \begin{cases}
+      0,& \text{if } j < J\\
+      \infty,& \text{if } j \geq J
+    \end{cases}
+    \nonumber
+\end{equation}
+where J is a well-defined boundary. So the walker has no chance of dying whilst
+within the well, but will die immediately once reaching the boundary. As
+explained in Section \ref{sec:TheoreticalBackground}, we expect that given
+sufficient time, all the walkers will reach the boundary and die. But in order
+to save computational resources, a maximum number of steps may also be defined,
+such that a walker will also die should they move that number of steps without
+reaching a boundary. This was not initially implemented, as it can introduce
+systemic errors, since there would be a disproportionate number of walkers dying
+on the maximum number of steps.
+
+Thus, the Schr\"{o}dinger equation inside a one-dimensional infinite square well
+is simply that of a free particle:
+\begin{equation}
+  \frac{-\hbar^2}{2m}\frac{d^2 \psi}{dx^2} = E\psi(x)
+  \nonumber
+\end{equation}
+where $x$ is the position of the walker. By making the substitution $x = J
+\times j/R$, such that $j=R$ corresponds to the walker being at the boundary, we
+obtain:
+\begin{equation}
+  \begin{split}
+    -\frac{\hbar^2}{2m}\frac{R^2}{J^2}\frac{d^2\psi}{dj^2} &= E\psi(x)\\
+    -\frac{1}{2}\frac{d^2\psi}{dj^2} &= \frac{mJ^2E}{\hbar^2R^2}\psi(x)
+  \end{split}
+  \nonumber
+\end{equation}
+
+If we compare this to Equation \ref{eq:randomwave}, allowing $a(j) = 0$, we see
+that:
+\begin{equation}
+  \begin{split}
+    \lambda &= \frac{mJ^2E}{\hbar^2R^2} \\
+    E &= \lambda R^2 \frac{\hbar^2}{mJ^2}
+  \end{split}
+  \nonumber
+\end{equation}
+
+So, by calculating the death rate $\lambda$, we can find the ground state energy
+of a particle in an infinite square well.
+
+But the known ground state of a particle in an infinite square well is
+$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$. This implies that we expect $\lambda
+R^2=\frac{\pi^2}{8}$ where R is the boundary of the well. Thus, we expect to
+find a $\lambda$ that is close to this theoretical value.
+
+To find the rate of death $\lambda$, we consider Equation \ref{eq:firsteq}. With
+some simple manipulation:
+\begin{equation}
+  \begin{split}
+    p(j, n) & = q(j) \exp(-\lambda n)\\
+    \log(p) & = \log(q \exp(-\lambda n)) \\
+    \log(p) & = -\lambda n + log(q)
+  \end{split}
+  \nonumber
+\end{equation}
+Thus, by plotting the logarithm of the probability of surviving $n$ steps
+against the number of steps $n$, we can obtain the death rate $\lambda$ from the
+gradient.
+
+Varying the boundary $J$ of the square well will affect the accuracy of the
+final answer, and this is investigated here.
 
@@
 But the probability of death $a(j)$ and the second derivative are so small, that
-their product is neglected. We also let $p(j,n) = q(j) exp(-\lambda n)$ so that:
+their product is neglected. We also let $p(j,n) = q(j) \exp(-\lambda n)$ so that:
 

### 2020-04-18 plotcpp.py
Added multi-line plot with increasing J
Need to move this code into a separate function

@@ -48,7 +48,7 @@ def exp_plot(data, show=True, skip=0, start=1):
         plt.ylabel('Probability of Death')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        plt.savefig("./Paper/images/exp_plot.pdf")
+        # plt.savefig("./Paper/images/exp_plot.pdf")
         plt.show()
     return popt[1]
 
@@ -80,7 +80,7 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
         plt.ylabel('Probability of Survival')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        plt.savefig("./Paper/images/cum_exp_plot.pdf")
+        # plt.savefig("./Paper/images/cum_exp_plot.pdf")
         plt.show()
 
     return popt[1]
@@ -109,7 +109,7 @@ def line_plot(data, show=True, skip=0, start=1):
         plt.ylabel('log(Probability of Death)')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        plt.savefig("./Paper/images/line_plot.pdf")
+        # plt.savefig("./Paper/images/line_plot.pdf")
         plt.show()
     return popt[1]
 
@@ -138,7 +138,7 @@ def cum_line_plot(data, show=True, skip=0, start=1):
         plt.ylabel('log(Probability of Survival)')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        plt.savefig("./Paper/images/cum_line_plot.pdf")
+        # plt.savefig("./Paper/images/cum_line_plot.pdf")
         plt.show()
     return popt[1]
 
@@ -192,14 +192,14 @@ if __name__ == "__main__":
         print(prob_arrest_cum_line * boundary**2)
         print(np.pi**2/8)
 
-        if True:
+        if False:
             values = []
             for i in range(10):
                 run_model(dimen,
-                        iteration,
-                        maxSteps=maxSteps,
-                        potential=potential,
-                        boundary=boundary)
+                          iteration,
+                          maxSteps=maxSteps,
+                          potential=potential,
+                          boundary=boundary)
                 data = np.loadtxt("data.dat")
                 prob_arrest_cum_line = cum_line_plot(data, show=False, skip=100, start=boundary)
                 print(prob_arrest_cum_line * boundary**2)
@@ -208,5 +208,71 @@ if __name__ == "__main__":
             gradient = np.average(values)
[…]

### 2020-04-18 Paper/main.tex
Rearranged figures and added captions

@@
 \usepackage{todonotes}
+\usepackage[caption=false]{subfig}
 
@@
 Random Walk simulations can be applied to calculate the ground state energies of
-Quantum Systems by solving the Schr\"{o}dinger equation. Consider a
+Quantum Systems by solving the Schr\"{o}dinger equation \todo{cite}. Consider a
 one-dimensional simple lattice system. A walker can start at a position labelled
@@
 specifically chosen $a(j)$. Initially, the $a(j)$ is chosen to be that of an
-infinite square well, that is:
+infinite square well \todo{cite}, that is:
 \begin{equation}
@@
 Thus, the Schr\"{o}dinger equation inside a one-dimensional infinite square well
-is simply that of a free particle:
+is simply that of a free particle \todo{cite}:
 \begin{equation}
@@
 But the known ground state of a particle in an infinite square well is
-$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$. This implies that we expect $\lambda
+$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \todo{cite}. This implies that we expect $\lambda
 R^2=\frac{\pi^2}{8}$ where R is the boundary of the well. Thus, we expect to
@@
 Varying the boundary $J$ of the square well will affect the accuracy of the
-final answer, and this is investigated here.
+final answer, and this is also investigated here.
 
@@
 
-Sample Text
+\begin{figure*}[ht!]
+  \centering
+  \subfloat[Histogram of probability of dying on particlar step]
+  {\includegraphics[width=0.5\textwidth]{images/exp_plot.pdf}
+  \label{fig:hist}}
+  \centering
+  \subfloat[Histogram of probability of dying on particular step in a logarithmic scale]
+  {\includegraphics[width=0.5\textwidth]{images/line_plot.pdf}
+    \label{fig:loghist}}
+  \caption{Histograms showing the Probability of dying on a particular step in
+    an infinite square well with $J = 20$. As can be seen, the peak is away from the
+    origin, as is expected since it is not likely for a walker to die on a step $n$
+    where $n < J$. The exponential decay after the peak is evident, implying a
+    straight line shape if plotted on a logarithmic scale, which can be seen on
+    the right hand side plot. In this logarithmic scale plot, the peak being away
+    from the origin is clearer.}
+  \label{fig:expplots}
+\end{figure*}
 
-\begin{figure}[H]%[!ht]
+\begin{figure*}[ht!]
+  \centering
+  \subfloat[Histogram of probability of surviving to at least a particlar step]
+  {\includegraphics[width=0.5\textwidth]{images/cum_exp_plot.pdf}
+  \label{fig:cumhist}}
+  \centering
+  \subfloat[Histogram of probability of surviving to at least a particular step
+  in a logarithmic scale]
+  {\includegraphics[width=0.5\textwidth]{images/cum_line_plot.pdf}
+  \label{fig:cumloghist}}
+  \caption{Histogram showing the Probability of surviving to at least a
+      particular step in an infinite square well with $J = 20$. This is a
+      cumulative sum of the bins in Figure \ref{fig:hist}. As can be seen, the
+      peak is at the origin, since it is certain that no walker will die on the
+      first step. An exponential decay curve provides a good fit, with an $R^2$
+      value of 0.9999998, very close to 1. Plotting on a logarithmic scale shows
+      the straight line fit, the gradient of which is $\lambda$, giving $\lambda
+      J^2 = 1.2334$, with a negligible error.}
+  \label{fig:cumplots}
+\end{figure*}
+
+\begin{figure}[!ht]
   \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/exp_plot.pdf}
-    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
-    \label{fig:exp_plot}
+    \includegraphics[width=0.45\textwidth]{images/multiplot.pdf}
+    \caption{Histogram plotted on a logarithmic scale showing the Probability of
+      surviving to at least a particualr step in different infinite square wells with
+      different boundaries $J$. The $\lambda J^2$ values for each are shown. The
+      values get closer to the theoretical value of $\frac{\pi^2}{8}$ as we increase
+      the size of the well. This is likely due to more walkers surviving to a higher
+      number of steps, as the well size is increased.}
+    \label{fig:multi_line_plot}
   \end{center}
@@
 
-\begin{figure}[H]%[!ht]
-  \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/line_plot.pdf}
-    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
-    \label{fig:line_plot}
-  \end{center}
-\end{figure}
-
-\begin{figure}[H]%[!ht]
-  \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/cum_exp_plot.pdf}
-    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
-    \label{fig:cum_exp_plot}
-  \end{center}
-\end{figure}
-
-\begin{figure}[H]%[!ht]
-  \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/cum_line_plot.pdf}
-    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
-    \label{fig:cum_line_plot}
-  \end{center}
-\end{figure}
-
-\begin{figure}[H]%[!ht]
+\begin{figure}[!ht]
   \begin{center}
     \includegraphics[width=0.45\textwidth]{images/cum_line_plot_cutoff.pdf}
-    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
+    \caption{Histogram plotted on a logarithmic scale showing the Probability of
+      surviving to at least a particular step in an infinite square well with $J
+      = 20$, and also introducing a maximum number of steps at 2000, after which
+      all walkers will die. This saves computational resources but introduces
+      some systematic error, as there will now be a disproportionately high
+      number of walkers in the 2000 steps bin.}
     \label{fig:cum_line_cutoff_plot}

### 2020-04-18 plotcpp.py
Added R^2 value and fit error calculations

@@ -60,7 +60,7 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
     plt.rc('text', usetex=True)
     plt.rc('font', family='serif')
 
-    hist = plt.hist(data, nbins, normed=True, align='mid')
+    hist = plt.hist(data, nbins, normed=False, align='mid')
     plt.clf()
 
     x = hist[1][skip:-1]
@@ -69,8 +69,9 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
     # normalising it myself since normed=True doesn't seem to work
     # y = y/np.sum(y)
     cum_y = np.cumsum(y[::-1])[::-1]
+    cum_y = cum_y/max(cum_y)
 
-    popt, _ = curve_fit(exp_curve, x, cum_y, p0=[1.28, 0.019])
+    popt, pcov = curve_fit(exp_curve, x, cum_y, p0=[1.28, 0.019])
 
     if show:
         # plt.plot(x, cum_y)
@@ -80,8 +81,15 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
         plt.ylabel('Probability of Survival')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
-        # plt.savefig("./Paper/images/cum_exp_plot.pdf")
+        plt.savefig("./Paper/images/cum_exp_plot.pdf")
         plt.show()
+
+    residuals = cum_y - exp_curve(x, *popt)
+    ss_res = np.sum(residuals**2)
+    ss_tot = np.sum((cum_y-np.mean(cum_y))**2)
+    r_squared = 1 - (ss_res / ss_tot)
+    print("R^2 value is: ", r_squared)
+    print("Gradient is: ", popt[1], " ± ", pcov[1])
 
     return popt[1]
 
@@ -128,7 +136,7 @@ def cum_line_plot(data, show=True, skip=0, start=1):
 
     cum_y = np.cumsum(y[::-1])[::-1]
 
-    popt, _ = curve_fit(exp_curve, x, cum_y, p0=[1.28, 0.019])
+    popt, pcov = curve_fit(exp_curve, x, cum_y, p0=[1.28, 0.019])
 
     if show:
         plt.yscale("log")
@@ -140,6 +148,14 @@ def cum_line_plot(data, show=True, skip=0, start=1):
         plt.legend()
         # plt.savefig("./Paper/images/cum_line_plot.pdf")
         plt.show()
+
+    residuals = cum_y - exp_curve(x, *popt)
[…]

### 2020-04-19 Paper/main.tex
Completed Results and Conclusion sections

@@
 
-\begin{figure}%[H]%[!ht]
+\begin{figure}%[H]%%[!ht]
   \begin{center}
     \includegraphics[width=0.45\textwidth]{images/cartoon.pdf}
-    \caption{Illustrations, graphs, and photographs may fit across both columns, if necessary. Your artwork must be in place in the article.}
+    \caption{Illustrations, graphs, and photographs may fit across both columns,
+      if necessary. Your artwork must be in place in the article.}
     \label{fig:cartoon}
@@
 reaching a boundary. This was not initially implemented, as it can introduce
-systemic errors, since there would be a disproportionate number of walkers dying
+systematic errors, since there would be a disproportionate number of walkers dying
 on the maximum number of steps.
@@
     \log(p) & = \log(q \exp(-\lambda n)) \\
-    \log(p) & = -\lambda n + log(q)
   \end{split}
@@
 \end{equation}
+
+\begin{equation}
+  \log(p) = -\lambda n + log(q)
+  \label{eq:straightline}
+\end{equation}
+
 Thus, by plotting the logarithm of the probability of surviving $n$ steps
@@
 \section{Results and Discussion}
+The simulation was first run for an infinite square well with boundary $J = 20$,
+with 1000000 walkers. The step on which each walker died was recorded and then
+the normalised histogram in Figure \ref{fig:hist} was constructed. The histogram
+has been normalised, and is hence a probability distribution showing the
+probability that a walker will die on a particular step. As we expect, the peak
+is far from the origin, since for a walker to die in an inifinite square well
+with $J=20$, they would have to walk at least 20 steps. It is also highly
+unlikely that a walker would walk 20 steps in the same direction
+consecutively. Thus, the peak is also at a number of steps greater than $J$. We
+expect the shape of the decay after the peak to be exponential. We can see this
+by plotting the histogram on a logarithmic scale.
 
-\begin{figure*}[ht!]
+Figure \ref{fig:loghist} presents the same histogram data with a logarithmic y
+scale. In this figure, a straight line is evident in the data, showing the decay
+was indeed exponential after the peak. The peak probability being away fro the
+origin is also clearer in this figure. Figure \ref{fig:loghist} shows a
+``widening'' of the straight line at higher step numbers. This is because there
+is a greater variance in the number of walkers surviving to this number as it is
+highly unlikely.
+
+By taking the cumulative sum of the histograms in Figure \ref{fig:expplots}, we
+can ensure the peak probability begins at the origin. Figure \ref{fig:cumplots}
+present the cumulative sums of the histograms. They represent the probability of
+surviving at least a particular number of steps. Hence, the peak probability of
+1 is at the origin, since there is a probability of 1 that a walker will survive
+the first step.
+
+Figure \ref{fig:cumhist} presents the cumulative summed histogram, with a fitted
+exponential curve of the form of Equation \ref{eq:firsteq}. The fit is very
+good, with $R^2 = 0.9999998$, very close to 1. There is also negligible
+numerical error in the fit, i.e. an error smaller than the quoted precision of
+the fit parameters. This is because the simulation was run for 1000000 walkers,
+providing a large sample size. Figure \ref{fig:cumloghist} presents the same
+histogram with a logarithmic y-scale and a fitted straight line of the form of
+Equation \ref{eq:straightline}. This fit has the same $R^2$ value, as it is
+simply the same fit on a different y-scale, and is thus equally good.
+
+We observe some fluctuation in the data in the higher steps. This is because
+there are so few walkers surviving to this many steps that there is more
+significant variance in their relative numbers. It is possible to remove this
+variance by introducing a cutoff number of steps, i.e. a maximum number of steps
+at which the walker will automatically die, regardless of whether they reached a
+boundary or not. Thus, there will not be such high variance in the number of
+walkers surviving to high number of steps. This is presented in Figure
+\ref{fig:cum_line_cutoff_plot}. While this fit is observed to be better, with a
+higher $R^2$ value, some systematic error has been introduced since there will now
+be a disproportionately high number of walkers dying at the cutoff step. Thus,
+the final $\lambda J^2$ value will be less accurate. On a faster computer, with
+more efficient code, it is possible to forgo the step cutoff and allow the
+simulation to run until all the walkers die. This may take much longer but will
+ensure there will not be such a systematic error introduced.
+
+We can use the gradient of the fitted line in Figure \ref{fig:cumloghist} as the
+$\lambda$ value, and compare $\lambda J^2$ with the theoretical value. However,
+to determine the reliability of the calculated value, it is necessary to repeat
+the procedure many times and take the average $\lambda$ and the standard
+deviation as the error.
+
+It is also necessary to investigate how varying the boundary $J$ affects the
+accuracy of the final answer. Figure \ref{fig:multi_line_plot} presents the
+cumulative summed histograms with their fitted lines for many different boundary
+$J$ values. No step cutoff was introduced. The calculated $\lambda J^2$ value is
+shown in the legend. \todo{truncate numbers} As shown, the gradient changes, but
+this is to be expected since the expected highest number of steps would increase
+as the boundary is larger, since there is more ``space'' for the walker to move
+before reaching a boundary. As shown in the legend, the calculated $\lambda J^2$
+values get closer and closer and closer to the theoretical value as $J$
+increases. This is due to the fact that as $J$ increases, there are more walkers
+surviving to larger number of steps. \todo{make plot of lambda J against J}.
+Thus, we can say that using a larger value of $J$ will result in a more
+accurate answer but will also be more computationally intensive and take
+longer. Thus, we make a tradeoff between speed and accuracy and choose $J=20$
+for the final investigation.
+
+Running the simulation 10 times and taking the average $\lambda J^2$ with error
+being standard deviation, we find: $\lambda J^2 = 1.2339 \pm 0.0008$. We quote
+the precision to the decimal place at which there is variation from the
+theoretical result of $1.2337$. We notice also that the error in the calculated
+answer is small (since there is not much variation between repeated simulations)
+and the theoretical result is within the range of the calculated answer.
+
+\todo{circular well}
+\begin{figure*}%[ht!]
   \centering
@@
 
-\begin{figure*}[ht!]
+\begin{figure*}%[ht!]
   \centering
@@
       the straight line fit, the gradient of which is $\lambda$, giving $\lambda
+\todo{fix centering of cum plot}
       J^2 = 1.2334$, with a negligible error.}
@@
 
-\begin{figure}[!ht]
+\begin{figure}%[!ht]
+  \begin{center}
+    \includegraphics[width=0.45\textwidth]{images/cum_line_plot_cutoff.pdf}
+    \caption{Histogram plotted on a logarithmic scale showing the Probability of
+      surviving to at least a particular step in an infinite square well with $J
+      = 20$, and also introducing a maximum number of steps at 2000, after which
+      all walkers will die. This saves computational resources but introduces
+      some systematic error, as there will now be a disproportionately high
+      number of walkers in the 2000 steps bin.}
+    \label{fig:cum_line_cutoff_plot}
+  \end{center}
+\end{figure}
+
+\begin{figure}%[!ht]
   \begin{center}
@@
 
-\begin{figure}[!ht]
-  \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/cum_line_plot_cutoff.pdf}
-    \caption{Histogram plotted on a logarithmic scale showing the Probability of
-      surviving to at least a particular step in an infinite square well with $J
-      = 20$, and also introducing a maximum number of steps at 2000, after which
-      all walkers will die. This saves computational resources but introduces
-      some systematic error, as there will now be a disproportionately high
-      number of walkers in the 2000 steps bin.}
-    \label{fig:cum_line_cutoff_plot}
-  \end{center}
-\end{figure}
-
 \section{Conclusions}
 
-Sample Text
+In this investigation we demonstrated a method of calculating ground state
+energies of a quantum system using Random Walk computational simulations. The
+investigation focussed on an Infinite Square Well, but is easily extended to a
+Symmetric potential. The simualation was written in C++ to maximise performance
+and is available at \todo{cite}.
+
+The investigation explored the effects of varying the size of the well in
+determining the ground state energy of a quantum system, and showed that this
+method is more effective for larger wells, i.e. wells with larger
+boundaries. This is because for wells with larger boundaries, the walker can
+take a larger number of steps on average before dying, and thus can populate
+larger step bins. Thus, this method produces data that is close to the
+theoretical result for larger infinite square wells.
+
+The general theoretical result for the ground state energy of an infinite square
+well is $\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ where $J$ is the boundary of the
+well, and this method allows for the calculation of $\lambda R^2
+\frac{\hbar^2}{mJ^2}$, where $R$ also corresponds to the boundary of the
+well. Thus, we expect our calculated result to be $\lambda R^2 = \lambda J^2 =
+\frac{\pi^2}{8}$.
+
+This method provided $\lambda J^2 = 1.2339 \pm 0.0008$, which is very close to
+the theoretical result.
+
+This method can be easily extended to multiple dimensions with only a linear
+increase in time complexity for each added dimension. Thus, while this method
+may not be very efficient for low number of dimensions, it quickly becomes
+effective at a higher number of dimensions.
 

### 2020-04-19 Paper/main.tex
Rewrote Theoretical Background section

@@
 % author names 
-\author{Sai Pandian, ID: 29899923}% <-this % stops a space
+\author{Sai Pandian, ID: 29899923}%
 
@@
 
-\begin{IEEEkeywords}
-keywords, temperature, xxxx equation, etc.
-\end{IEEEkeywords}
+\section{Introduction}
+\IEEEPARstart{T}{he} developments in computer power in recent years has opened
+up the possibility for novel computational solutions to many problems that were
+otherwise limited. We now have access to computers that can numerically solve
+problems and run simulations that were previously too computationally intensive
+to do.
 
-\section{Introduction}
-% Here we have the typical use of a "W" for an initial drop letter
-% and "RITE" in caps to complete the first word.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
+One such problem is the calculation of the ground state energies of different
+quantum systems. Many methods exist for solving these problems, using both
+classical and quantum computational approaches. Whilst generally it may be true
+that Quantum computating approahes are more suited to solving such problems
+\cite{Mazzola}, these approaches are still in infancy and are not readily
+accessible. Thus, there exist an abundance of classical computing approaches,
+such as the Variational-Relaxiation algorithm \cite{Schroeder2017}. This is a
+particularly useful algorithm for two-dimensional systems with non-separable
+potentials but quickly becomes difficult to implement for more complex systems.
 
-\IEEEPARstart{R}{andom} walks are a simple model of motion in which a path is
-described as a succession of steps with each step being in a random direction on
-some vector space. Random walks are useful in modelling many physical processes
-that are perceived as having a pseudo-random mechanism \todo{cite}. Their
-applications range from Biology to the Stock Market. This paper aims to explore
-how Random Walk Simulations can be implemented to calculate the ground state
-energies of different quantum systems. \todo{more}
+In this investigation, I explore an alternative Monte Carlo method using Random
+Walk simulations, and demonstrate its efficacy with simple systems.
 
@@
 
-Random walks work descibe motion as a series of steps, with the direction of
-each step being random. Figure \ref{fig:cartoon} demonstrates this concept by
-considering a one-dimensional line. On this line, the ``walker'' starts at the
-origin, and walks a total of 20 steps. The walker at each step has a equal
-chance of stepping forwards, or stepping backwards.
+\subsection{Random Walk Simulations}
+
+Random walks descibe motion as a series of steps in some vector space, with the
+direction of each step being random, i.e. with there being an equal likelihood
+of a step in each possible direction. Consider a simple 1-dimensional line and a
+walker standing at a point labelled the origin. The walker takes 20 steps, the
+direction of each step (forwards or backwards on the line) is random. The
+position of the walker at each step is shown in Figure \ref{fig:cartoon}.
 
@@
     \includegraphics[width=0.45\textwidth]{images/cartoon.pdf}
-    \caption{Illustrations, graphs, and photographs may fit across both columns,
-      if necessary. Your artwork must be in place in the article.}
+    \caption{The position of a walker at each step in a 20-step random walk
+      simulation. The average position of the walker does not necessarily remain
+      at the origin as one might naively expect. Instead it is normal for the
+      walker to finish the walk at some distance from the origin, as shown here.}
     \label{fig:cartoon}
@@
 
-As can be seen from the figure, it is not uncommon for the average position of
+As we can see from the figure, it is not uncommon for the average position of
 the walker to be away from the origin once the walk has concluded. This is
@@
 each extra dimension, one extra random number must be drawn. This gives a linear
-increase in time-complexity, which is convenient for long computations.
+increase in time-complexity, which is convenient for more complex systems.
 
-Random Walk simulations can be applied to calculate the ground state energies of
-Quantum Systems by solving the Schr\"{o}dinger equation \todo{cite}. Consider a
-one-dimensional simple lattice system. A walker can start at a position labelled
-the origin, and then proceed in a random walk. The random walk concludes after a
-certain number of steps or if the walker ``dies'' on a particular step. The
-probability that the walker will die is dependent on a defined potential at that
-point. For example, in an infinite square well system, the potential is 0 within
-a well, and infinite outside the well. So the walker will have no chance of
-dying whilst inside the well, but will die if they step outside.
+\subsection{Application to Quantum Systems}
+
+This investigation applied Random walk simulations to calculate the ground state
+energies of Quantum Systems by solving the Schr\"{o}dinger equation, as shown in
+\todo{cite}.
+
+We can extend the simple one-dimensional line model from Figure
+\ref{fig:cartoon} to a quantum system by imagining it as a one-dimensional
+simple lattice system. A walker can start at a position labelled the origin, and
+then proceed in a random walk. The random walk concludes if the walker ``dies''
+on a particular step. The probability that the walker will die is dependent on a
+defined potential at that point. For example, in an infinite square well system,
+the potential is 0 within a well, and infinite outside the well. So the walker
+will have no chance of dying whilst inside the well, but will die if they step
+outside.
 
@@
 $j$ after $n$ steps and $a(j)$ as the probability that the walker will die at
-position $j$. If we say:
+position $j$. Thus, for this to be the case, the walker would have had position
+$j\pm1$ after $n-1$ steps. Thus, we can say:
+
+\begin{equation}
+  p(j, n+1) =  \frac{1}{2}(1-a(j))(p(j-1,n) + p(j+1,n))
+  \nonumber
+\end{equation}
+
+If $a(j)$ is small and $n$ is large, we can use Taylor's expansion to expand
+each term in this expression and obtain a differential equation. If we then
+make the ansatz substitution:
 
@@
 \end{equation}
-where $q(j)$ is an arbitrary function and $\lambda$ is the rate of death, then:
+where $q(j)$ is an arbitrary function and $\lambda$ is the rate of death, then
+we find:
+
 \begin{equation}
@@
 \end{equation}
+The full derivation is taken from \cite{MarcusNewton2020} and is shown in
+Appendix \ref{appendix:derivation}. Notice that Equation \ref{eq:randomwave} is
+in the form of the Schr\"{o}dinger equation:
 
-The full derivation is taken from \todo{cite} and is shown in Appendix
-\ref{appendix:derivation}.
-
-Notice that Equation \ref{eq:randomwave} is in the form of a wave equation,
-specifically the Schr\"{o}dinger equation:
 \begin{equation}
@@
 see that the probability of death $a(j)$ is related to the potential $V(r)$,
-and the rate of death $\lambda$ is related to the Energy $E$. Thus, by running
-the simulation for a particular potential (i.e. rate of death), one can
-determine the ground state energy of a system by calculating the rate of
-death. This is the technique employed in this paper.
+and the rate of death $\lambda$ is related to the Energy $E$.
+
+We can extend this to an infinite square well by choosing our probability of
+death such that:
+
+\begin{equation}
+  \label{eq:squarewell}
+    a(j) =
+    \begin{cases}
+      0,& \text{if } j < J\\
+      \infty,& \text{if } j \geq J
+    \end{cases}
+    \nonumber
+\end{equation}
+where J is a well-defined boundary. So the walker cannot die inside the well but
+wil immediately die when they step outside, which we expect will definitely
+happen given sufficient time. Inside the well, the potential is simply that of a
+free particle:
+
+\begin{equation}
+  \frac{-\hbar^2}{2m}\frac{d^2 \psi}{dx^2} = E\psi(x)
+  \nonumber
+\end{equation}
+where $x$ is the position of the walker. By making the substitution
+$x=J\frac{j}{R}$, such that $j=R$ corresponds to the walker being at the
+boundary, we find:
+
+\begin{equation}
+  \begin{split}
+    -\frac{\hbar^2}{2m}\frac{R^2}{J^2}\frac{d^2\psi}{dj^2} &= E\psi(x)\\
+    -\frac{1}{2}\frac{d^2\psi}{dj^2} &= \frac{mJ^2E}{\hbar^2R^2}\psi(x)
+  \end{split}
+  \nonumber
+\end{equation}
+If we compare this to Equation \ref{eq:randomwave}, allowing $a(j) = 0$ inside
+the well, we see that:
+
+\begin{equation}
+  E = \lambda R^2 \frac{\hbar^2}{mJ^2}
+  \nonumber
+\end{equation}
+where only $\lambda$ is an unknown quantity. Thus, by calculating rate of death
+$\lambda$, we can calculate the ground state energy of the infinite square
+well. The known ground state energy of an infnite square well is
+$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \todo{cite}, so we expect to find $\lambda
+R^2$ close to $\frac{\pi}{8}$.
 
@@
 
-The Random Walk is implemented computationally \todo{cite} and is extensible
+The Random walk is implemented computationally \todo{cite} and is extensible
 to multiple dimensions. For a $N$-dimensional lattice, at each point there are
@@
 was chosen as it is a very fast implementation of a pRNG \todo{cite} and it
-passes many statistical randomness tests \todo{cite}, having a very large
+passes many statistical randomness tests \todo{cite}, and has a very large
 period of $2^{19937-1}$.
@@
 
-If we compare this to Equation \ref{eq:randomwave}, allowing $a(j) = 0$, we see
-that:
+If we compare this to Equation \ref{eq:randomwave}, allowing $a(j) = 0$ inside
+the well, we see that:
 \begin{equation}
@@
       the straight line fit, the gradient of which is $\lambda$, giving $\lambda
-\todo{fix centering of cum plot}
       J^2 = 1.2334$, with a negligible error.}
@@
 \end{figure*}
+
+\todo{fix centering of cum plot}
 
@@
 In this investigation we demonstrated a method of calculating ground state
-energies of a quantum system using Random Walk computational simulations. The
+energies of a quantum system using Random walk computational simulations. The
 investigation focussed on an Infinite Square Well, but is easily extended to a
@@
 
-This method provided $\lambda J^2 = 1.2339 \pm 0.0008$, which is very close to
-the theoretical result.
+This method provided $\lambda J^2 = 1.2339 \pm 0.0008$, which lies within the
+range of the theoretical result.
 
@@
 \appendices
-\section{Random Walk Schr\"{o}dinger Equation Derivation}
+\section{Random walk Schr\"{o}dinger Equation Derivation}
 \label{appendix:derivation}

### 2020-04-19 Paper/main.tex
Rewrote Method section based on feedback

@@
 % paper title
-\title{Using Random Walk Simulations to Calculate Ground State Energies in Quantum Physics}
+\title{Using Random Walk Simulations to Calculate Ground State Energies in
+  Quantum Physics}
 
@@
 happen given sufficient time. Inside the well, the potential is simply that of a
-free particle:
+free particle \todo{cite}:
 
@@
 
-\section{Method}
-
-The Random walk is implemented computationally \todo{cite} and is extensible
-to multiple dimensions. For a $N$-dimensional lattice, at each point there are
-$2N$ possible directions for the walker to move. So a direction is selected
-randomly using a Mersenne Twister pseudorandom number generator (pRNG). This algorithm
-was chosen as it is a very fast implementation of a pRNG \todo{cite} and it
-passes many statistical randomness tests \todo{cite}, and has a very large
-period of $2^{19937-1}$.
-
-The random walk ends when a walker dies, with a
-specifically chosen $a(j)$. Initially, the $a(j)$ is chosen to be that of an
-infinite square well \todo{cite}, that is:
-\begin{equation}
-  \label{eq:squarewell}
-    a(j) =
-    \begin{cases}
-      0,& \text{if } j < J\\
-      \infty,& \text{if } j \geq J
-    \end{cases}
-    \nonumber
-\end{equation}
-where J is a well-defined boundary. So the walker has no chance of dying whilst
-within the well, but will die immediately once reaching the boundary. As
-explained in Section \ref{sec:TheoreticalBackground}, we expect that given
-sufficient time, all the walkers will reach the boundary and die. But in order
-to save computational resources, a maximum number of steps may also be defined,
-such that a walker will also die should they move that number of steps without
-reaching a boundary. This was not initially implemented, as it can introduce
-systematic errors, since there would be a disproportionate number of walkers dying
-on the maximum number of steps.
-
-Thus, the Schr\"{o}dinger equation inside a one-dimensional infinite square well
-is simply that of a free particle \todo{cite}:
-\begin{equation}
-  \frac{-\hbar^2}{2m}\frac{d^2 \psi}{dx^2} = E\psi(x)
-  \nonumber
-\end{equation}
-where $x$ is the position of the walker. By making the substitution $x = J
-\times j/R$, such that $j=R$ corresponds to the walker being at the boundary, we
-obtain:
-\begin{equation}
-  \begin{split}
-    -\frac{\hbar^2}{2m}\frac{R^2}{J^2}\frac{d^2\psi}{dj^2} &= E\psi(x)\\
-    -\frac{1}{2}\frac{d^2\psi}{dj^2} &= \frac{mJ^2E}{\hbar^2R^2}\psi(x)
-  \end{split}
-  \nonumber
-\end{equation}
-
-If we compare this to Equation \ref{eq:randomwave}, allowing $a(j) = 0$ inside
-the well, we see that:
-\begin{equation}
-  \begin{split}
-    \lambda &= \frac{mJ^2E}{\hbar^2R^2} \\
-    E &= \lambda R^2 \frac{\hbar^2}{mJ^2}
-  \end{split}
-  \nonumber
-\end{equation}
-
-So, by calculating the death rate $\lambda$, we can find the ground state energy
-of a particle in an infinite square well.
-
-But the known ground state of a particle in an infinite square well is
-$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \todo{cite}. This implies that we expect $\lambda
-R^2=\frac{\pi^2}{8}$ where R is the boundary of the well. Thus, we expect to
-find a $\lambda$ that is close to this theoretical value.
-
 To find the rate of death $\lambda$, we consider Equation \ref{eq:firsteq}. With
@@
 against the number of steps $n$, we can obtain the death rate $\lambda$ from the
-gradient.
+gradient of the line.
 
-Varying the boundary $J$ of the square well will affect the accuracy of the
-final answer, and this is also investigated here.
+\section{Method}
+We implemented the Random Walk simulation computationally in
+C++ in order to optimise the performance of the simulation, and thereby allow
+for a larger number of iterations and larger potential wells. The source code is
+available \cite{Pandian}. The simulation is easily extensible to multiple
+dimensions with a linear increase in time-complexity as the number of dimensions
+increases, but this investigation focused on a one-dimensional system.
+
+The random direction is selected using a pseudorandom number generator (pRNG)
+known as the Mersenne Twister. This algorithm was chosen as it is a very fast
+implementation of a pRNG \cite{Route2017}, passes many statistical randomness
+tests \cite{Bellamy2013}, and has a very large period of $2^{19937}-1$.
+
+We initially ran the simulation for a boundary of $J = 20$, with $1000000$
+walkers. The step on which each walker died was recorded so that a probability
+distribution showing the likelihood of dying on a particular step could be
+constructed.
+
+We then consider the probability that a walker will survive $n$ steps, and use
+the relationship between the number of walkers surviving $n$ steps and $n$ to
+determine the rate of death $\lambda$, as shown in Equation \ref{eq:straightline}.
+
+One method of reducing the computing time of the simulation is to introduce a
+maximum number of steps. The walker will die if they reach the boundary of the
+well, or if they reach this maximum number of steps, whichever happens
+first. However, this will introduce some systematic error into the simulation,
+as there will be a disproportionately high number of walkers dying on the
+maximum number of steps. We also investigated these effects here.
+
+We expect to see an effect on the accuracy of our final ground state depending
+on the size of the infinite well. We investigate these effects by comparing the
+calculated ground state energy to the theoretical energy for different sized wells.
 

### 2020-04-19 Paper/main.tex
Rewrote Results section

@@
 \usepackage[style=ieee]{biblatex} 
-\bibliography{random_walk.bib}    %your file created using JabRef
+\bibliography{random_walk.bib}
 
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
-\usepackage{graphicx}  %needed to include png, eps figures
+\usepackage{graphicx}  % needed to include png, eps figures
 \usepackage{float}  % used to fix location of images i.e.\begin{figure}[H]
@@
 \section{Results and Discussion}
-The simulation was first run for an infinite square well with boundary $J = 20$,
-with 1000000 walkers. The step on which each walker died was recorded and then
-the normalised histogram in Figure \ref{fig:hist} was constructed. The histogram
-has been normalised, and is hence a probability distribution showing the
-probability that a walker will die on a particular step. As we expect, the peak
-is far from the origin, since for a walker to die in an inifinite square well
-with $J=20$, they would have to walk at least 20 steps. It is also highly
-unlikely that a walker would walk 20 steps in the same direction
-consecutively. Thus, the peak is also at a number of steps greater than $J$. We
-expect the shape of the decay after the peak to be exponential. We can see this
-by plotting the histogram on a logarithmic scale.
-
-Figure \ref{fig:loghist} presents the same histogram data with a logarithmic y
-scale. In this figure, a straight line is evident in the data, showing the decay
-was indeed exponential after the peak. The peak probability being away fro the
-origin is also clearer in this figure. Figure \ref{fig:loghist} shows a
-``widening'' of the straight line at higher step numbers. This is because there
-is a greater variance in the number of walkers surviving to this number as it is
-highly unlikely.
-
-By taking the cumulative sum of the histograms in Figure \ref{fig:expplots}, we
-can ensure the peak probability begins at the origin. Figure \ref{fig:cumplots}
-present the cumulative sums of the histograms. They represent the probability of
-surviving at least a particular number of steps. Hence, the peak probability of
-1 is at the origin, since there is a probability of 1 that a walker will survive
-the first step.
-
-Figure \ref{fig:cumhist} presents the cumulative summed histogram, with a fitted
-exponential curve of the form of Equation \ref{eq:firsteq}. The fit is very
-good, with $R^2 = 0.9999998$, very close to 1. There is also negligible
-numerical error in the fit, i.e. an error smaller than the quoted precision of
-the fit parameters. This is because the simulation was run for 1000000 walkers,
-providing a large sample size. Figure \ref{fig:cumloghist} presents the same
-histogram with a logarithmic y-scale and a fitted straight line of the form of
-Equation \ref{eq:straightline}. This fit has the same $R^2$ value, as it is
-simply the same fit on a different y-scale, and is thus equally good.
-
-We observe some fluctuation in the data in the higher steps. This is because
-there are so few walkers surviving to this many steps that there is more
-significant variance in their relative numbers. It is possible to remove this
-variance by introducing a cutoff number of steps, i.e. a maximum number of steps
-at which the walker will automatically die, regardless of whether they reached a
-boundary or not. Thus, there will not be such high variance in the number of
-walkers surviving to high number of steps. This is presented in Figure
-\ref{fig:cum_line_cutoff_plot}. While this fit is observed to be better, with a
-higher $R^2$ value, some systematic error has been introduced since there will now
-be a disproportionately high number of walkers dying at the cutoff step. Thus,
-the final $\lambda J^2$ value will be less accurate. On a faster computer, with
-more efficient code, it is possible to forgo the step cutoff and allow the
-simulation to run until all the walkers die. This may take much longer but will
-ensure there will not be such a systematic error introduced.
-
-We can use the gradient of the fitted line in Figure \ref{fig:cumloghist} as the
-$\lambda$ value, and compare $\lambda J^2$ with the theoretical value. However,
-to determine the reliability of the calculated value, it is necessary to repeat
-the procedure many times and take the average $\lambda$ and the standard
-deviation as the error.
-
-It is also necessary to investigate how varying the boundary $J$ affects the
-accuracy of the final answer. Figure \ref{fig:multi_line_plot} presents the
-cumulative summed histograms with their fitted lines for many different boundary
-$J$ values. No step cutoff was introduced. The calculated $\lambda J^2$ value is
-shown in the legend. \todo{truncate numbers} As shown, the gradient changes, but
-this is to be expected since the expected highest number of steps would increase
-as the boundary is larger, since there is more ``space'' for the walker to move
-before reaching a boundary. As shown in the legend, the calculated $\lambda J^2$
-values get closer and closer and closer to the theoretical value as $J$
-increases. This is due to the fact that as $J$ increases, there are more walkers
-surviving to larger number of steps. \todo{make plot of lambda J against J}.
-Thus, we can say that using a larger value of $J$ will result in a more
-accurate answer but will also be more computationally intensive and take
-longer. Thus, we make a tradeoff between speed and accuracy and choose $J=20$
-for the final investigation.
-
-Running the simulation 10 times and taking the average $\lambda J^2$ with error
-being standard deviation, we find: $\lambda J^2 = 1.2339 \pm 0.0008$. We quote
-the precision to the decimal place at which there is variation from the
-theoretical result of $1.2337$. We notice also that the error in the calculated
-answer is small (since there is not much variation between repeated simulations)
-and the theoretical result is within the range of the calculated answer.
-
-\todo{circular well}
-\begin{figure*}%[ht!]
-  \centering
-  \subfloat[Histogram of probability of dying on particlar step]
-  {\includegraphics[width=0.5\textwidth]{images/exp_plot.pdf}
-  \label{fig:hist}}
-  \centering
-  \subfloat[Histogram of probability of dying on particular step in a logarithmic scale]
-  {\includegraphics[width=0.5\textwidth]{images/line_plot.pdf}
-    \label{fig:loghist}}
-  \caption{Histograms showing the Probability of dying on a particular step in
-    an infinite square well with $J = 20$. As can be seen, the peak is away from the
-    origin, as is expected since it is not likely for a walker to die on a step $n$
-    where $n < J$. The exponential decay after the peak is evident, implying a
-    straight line shape if plotted on a logarithmic scale, which can be seen on
-    the right hand side plot. In this logarithmic scale plot, the peak being away
-    from the origin is clearer.}
-  \label{fig:expplots}
-\end{figure*}
 
@@
   \caption{Histogram showing the Probability of surviving to at least a
-      particular step in an infinite square well with $J = 20$. This is a
-      cumulative sum of the bins in Figure \ref{fig:hist}. As can be seen, the
-      peak is at the origin, since it is certain that no walker will die on the
-      first step. An exponential decay curve provides a good fit, with an $R^2$
-      value of 0.9999998, very close to 1. Plotting on a logarithmic scale shows
-      the straight line fit, the gradient of which is $\lambda$, giving $\lambda
-      J^2 = 1.2334$, with a negligible error.}
+    particular step in an infinite square well with $J = 20$. The peak of 1 does
+    not start at the origin but at step 100. This is because these steps were
+    neglected in the plot as prior to this step the exponential shape is less
+    clear, as explained by Figure \ref{fig:hist}. An exponential decay curve
+    provides a good fit, with an $R^2$ value of 0.9999998, very close to
+    1. Plotting on a logarithmic scale shows the straight line fit, the gradient
+    of which is $\lambda$, giving $\lambda J^2 = 1.2334$, with a negligible
+    error. The fluctuation in the higher step number regions is due to the large
+    variance in the small number of walkers that die at these steps.}
   \label{fig:cumplots}
@@
 
-\todo{fix centering of cum plot}
+The simulation was first run for an infinite square well with boundary $J=20$
+with 1000000 walkers. The number of walkers surviving at each step was recorded
+and the histograms in Figure \ref{fig:cumplots} were created. The probability
+that a walker will survive at a particular step is simply the 1 minus the
+normalised cumulative sum of walkers dying at each step. The curve has been
+fitted with an exponential function of the form in Equation
+\ref{eq:firsteq}. This results in a very good fit, with an $R^2$ value of
+0.9999998, indicating the data does not vary much from the curve of best
+fit. This is likely due to the very large number of walkers used in this
+experiment, as allowed by the performant C++ implementation.
+
+We can see this better in Figure \ref{fig:cumloghist}, which is the same
+exponential plot fitted on a logarithmic scale. The closeness of the data to the
+line of best fit is evident here. The error in the fitted parameters is
+negligible, as shown by the $R^2$ value. The gradient of the fitted line is
+taken to be $\lambda$ and thus allows us to calculate $\lambda J^2 = 1.2334$,
+compared to the theoretical value of $\frac{\pi^2}{8} = 1.2337$, quoting both
+values to the precision at which they vary. Since the numerical error in the
+fits is negligible, it cannot be propagated into an error in the final
+answer. Thus, we get the error in the final answer from repeated runs of the
+simulation and taking the standard deviation of the many values.
+
+As we can observe in Figure \ref{fig:cumhist}, the peak of the curve does not
+lie at the origin as we might expect from the fact that all walkers should
+survive at least the first step. The reason for this is twofold:
+\begin{itemize}
+\item For a well with boundary $J$, it is not possible for the walker to die in
+  a number of steps less than $J$
+\item It is highly unlikely that the walker will die at a number of steps
+  greater than but still close to $J$ since it would require walking in the same
+  direction a dispropotionate number of times.
+\end{itemize}
 
@@
   \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/cum_line_plot_cutoff.pdf}
-    \caption{Histogram plotted on a logarithmic scale showing the Probability of
-      surviving to at least a particular step in an infinite square well with $J
-      = 20$, and also introducing a maximum number of steps at 2000, after which
-      all walkers will die. This saves computational resources but introduces
-      some systematic error, as there will now be a disproportionately high
-      number of walkers in the 2000 steps bin.}
-    \label{fig:cum_line_cutoff_plot}
+    \includegraphics[width=0.45\textwidth]{images/exp_plot.pdf}
+    \caption{The probability of dying on a particular step in an infnite square
+      well with $J=20$. As can be seen, the peak is away from the origin. This
+      is because, for a well with boundary $J$, the minimum number of steps a
+      walker must take is $J$. However, it is still unlikely that the walker
+      will die on this minimum number of steps, as then the walker must walk in
+      the same direction every time. Thus, the most probable step for the walker
+      to die on is greater than $J$. It is for this reason that the exponential
+      decay does not begin at the origin in Figure \ref{fig:cumhist}, meaning
+      some earlier steps must be neglected in order to achieve a better fit.}
+    \label{fig:hist}
   \end{center}
@@
 
+These effects are evident in Figure \ref{fig:hist}, which presents the
+probability that a walker will die at a particular number of steps. We can see
+that the peak of the curve is very clearly at a step that is greater than 20,
+which was the $J$ value used in this simulation. Thus, for low step numbers, the
+shape of the curve is not exponential. For this reason we used a simple
+algorithm to identify a suitable number of steps to skip before fitting the
+exponential curve. It is for this reason that the histogram in Figure
+\ref{fig:cumhist} does not start at the origin.
+
 \begin{figure}%[!ht]
   \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/multiplot.pdf}
+    \includegraphics[width=0.45\textwidth]{images/line_plot.pdf}
+    \caption{The probability of dying on a particular step in an infnite square
+      well with $J=20$, plotted on a logarithmic scale. As explained for Figure
+      \ref{fig:hist}, the peak probability is on a step greater than $J$. This
+      is clear in this plot. It is also evident that there is significantly more
+      spread in the points at higher steps. This is due to there being
+      significantly fewer walkers dying on these steps, so the relative
+      differences are higher. This explains the fluctuations seen at higher
+      steps in Figure \ref{fig:cumloghist}.}
+    \label{fig:loghist}
+  \end{center}
+\end{figure}
+
+We observe some fluctuation in the data in the higher steps in Figure
+\ref{fig:cumloghist}. This is because there are so few walkers surviving to this
+many steps that there is more significant variance in their relative numbers. We
+can observe this in Figure \ref{fig:loghist}. At higher step numbers, the spread
+is clearly larger due to the greater relative variance in the small number of
+walkers surviving to this many steps. When this data is cumulatively summed to
+calculate the probability of survival shown in Figure \ref{fig:cumloghist}, the
+spread is present as the fluctuations.
+
+\begin{figure*}%[ht!]
+  \centering
+  \subfloat[Probability of dying on a particlar step with a step cutoff]
+  {\includegraphics[width=0.5\textwidth]{images/exp_plot_cutoff.pdf}
+  \label{fig:expcutoff}}
+  \centering
+  \subfloat[Probability of surviving to at least a particular step in a
+  logarithmic scale with a step cutoff]
+  {\includegraphics[width=0.5\textwidth]{images/cum_line_plot_cutoff.pdf}
+  \label{fig:cum_line_cutoff_plot}}
+  \caption{Histograms showing the results of the simulation when a maximm number
+  of steps is introduced. If a walker reaches this number of steps, they
+  automatically die, regardless of position. This results in a
+  disproportionately high number of walkers dying at this maximum number, 2000
+  in this case, as shown by Figure \ref{fig:expcutoff}. However, this results in
+  no fluctuation at higher number of steps, as shown in Figure
+  \ref{fig:cum_line_cutoff_plot}, though some systematic error is introduced
+  through this method.}
+  \label{fig:cutoffplots}
+\end{figure*}
+
+It is possible to remove this variance by introducing a cutoff number of steps,
+i.e. a maximum number of steps at which the walker will automatically die,
+regardless of whether they reached a boundary or not. Thus, there will not be
+such high variance in the number of walkers surviving to high number of
+steps. This is presented in Figure \ref{fig:cum_line_cutoff_plot}. While this
+fit is observed to be better, with a higher $R^2$ value, some systematic error
+has been introduced since there will now be a disproportionately high number of
+walkers dying at the cutoff step as can be seen in Figure
+\ref{fig:expcutoff}. Thus, the final $\lambda J^2$ value will be less
+accurate. On a faster computer, with more efficient code, it is possible to
+forgo the step cutoff and allow the simulation to run until all the walkers
+die. This may take much longer but will ensure there will not be such a
+systematic error introduced. This is the method used in this investigation.
+
+It is also necessary to investigate how varying the boundary $J$ affects the
+accuracy of the final answer. Figure \ref{fig:multi_line_plot} presents the
+cumulative summed histograms with their fitted lines for many different boundary
+$J$ values. No step cutoff was introduced. The calculated $\lambda J^2$ value is
+shown in the legend. As shown, the gradient changes, but this is to be expected
+since the expected highest number of steps would increase as the boundary is
+larger, since there is more space for the walker to move before reaching a
+boundary. As shown in the legend, the calculated $\lambda J^2$ values get closer
+and closer and closer to the theoretical value as $J$ increases. This is due to
+the fact that as $J$ increases, there are more walkers surviving to larger
+number of steps. Thus, we can say that using a larger value of $J$ will result
+in a more accurate answer but will also be more computationally intensive and
+take longer. Thus, we make a tradeoff between speed and accuracy and choose
+$J=20$ for the final investigation.
+
+Running the simulation 10 times and taking the average $\lambda J^2$ with error
+being standard deviation, we find:
+\begin{equation}
+  \lambda J^2 = 1.2339 \pm 0.0008
+  \nonumber
+\end{equation}
+We quote the precision to the decimal place at which there is variation from the
+theoretical result of $1.2337$. We notice that the error in the calculated
+answer is small (since there is not much variation between repeated simulations)
+and the theoretical result is within the range of the calculated answer.
+
+\todo{circular well}
+
+\begin{figure}%[!ht]
+  \begin{center}
+    \includegraphics[width=0.45\textwidth]{images/multiplot1.pdf}
     \caption{Histogram plotted on a logarithmic scale showing the Probability of
-      surviving to at least a particualr step in different infinite square wells with
-      different boundaries $J$. The $\lambda J^2$ values for each are shown. The
-      values get closer to the theoretical value of $\frac{\pi^2}{8}$ as we increase
-      the size of the well. This is likely due to more walkers surviving to a higher
+      surviving to at least a particualr step in different infinite square wells
+      with different boundaries $J$. The simulations were run with $10000$
+      walkers The $\lambda J^2$ values for each are shown. The values get closer
+      to the theoretical value of $\frac{\pi^2}{8} = 1.2337$ as we increase the
+      size of the well. This is likely due to more walkers surviving to a higher
       number of steps, as the well size is increased.}
@@
 
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-
 \appendices
@@
 \label{appendix:derivation}
-Let us denote the probability that the walker is at position $j$ after $n$ steps
-as $p(j,n)$ and the probabilty that the walker will die at position $j$ as
-$a(j)$. We will denote the position-step number coordinates as $[j, n]$. Thus,
-for a walker to have coordinates $[j, n+1]$, in the previous step, they must have
-had coordinates $[j \pm 1, n]$. So we can say:
+Consider a one-dimensional lattice upon which a walker is undergoing a random
+walker. Let us denote the probability that the walker is at position $j$ after
+$n$ steps as $p(j,n)$ and the probabilty that the walker will die at position
+$j$ as $a(j)$. We will denote the position-step number coordinates as $[j,
+n]$. Thus, for a walker to have coordinates $[j, n+1]$, in the previous step,
+they must have had coordinates $[j \pm 1, n]$. So we can say:
 

### 2020-04-19 Paper/main.tex
Rewrote Conclusions sections

@@
 % main body of the paper.
+  In this paper, we present a novel way of calculating ground state energies for
+  a quantum simulation using a Random Walk Monte Carlo simulation.
 \end{abstract}
@@
 
-In this investigation, I explore an alternative Monte Carlo method using Random
+In this investigation, we explore an alternative Monte Carlo method using Random
 Walk simulations, and demonstrate its efficacy with simple systems.
@@
 
-\begin{figure}%[H]%%[!ht]
+\begin{figure}[H]%[!ht]
   \begin{center}
@@
 energies of Quantum Systems by solving the Schr\"{o}dinger equation, as shown in
-\todo{cite}.
+\cite{Ceperley1983}.
 
@@
 happen given sufficient time. Inside the well, the potential is simply that of a
-free particle \todo{cite}:
+free particle \cite{Bransden2003}:
 
@@
 well. The known ground state energy of an infnite square well is
-$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \todo{cite}, so we expect to find $\lambda
+$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \cite{Davies1998}, so we expect to find $\lambda
 R^2$ close to $\frac{\pi}{8}$.
@@
 
-\begin{figure*}%[ht!]
+\begin{figure*}[ht!]
   \centering
@@
 
-\begin{figure}%[!ht]
+\begin{figure}[H]%[!ht]
   \begin{center}
@@
 
+\begin{figure}[!ht]
+  \begin{center}
+    \includegraphics[width=0.45\textwidth]{images/multiplot1.pdf}
+    \caption{Histogram plotted on a logarithmic scale showing the Probability of
+      surviving to at least a particular step in different infinite square wells
+      with different boundaries $J$. The simulations were run with $10000$
+      walkers The $\lambda J^2$ values for each are shown. The values get closer
+      to the theoretical value of $\frac{\pi^2}{8} = 1.2337$ as we increase the
+      size of the well. This is likely due to more walkers surviving to a higher
+      number of steps, as the well size is increased.}
+    \label{fig:multi_line_plot}
+  \end{center}
+\end{figure}
+
 It is also necessary to investigate how varying the boundary $J$ affects the
@@
 
-Running the simulation 10 times and taking the average $\lambda J^2$ with error
-being standard deviation, we find:
+Running the simulation 10 times with 1000000 walkers in an infinite square well
+with $J=20$ and taking the average $\lambda J^2$ with error being standard
+deviation, we find:
 \begin{equation}
@@
 
-\todo{circular well}
-
-\begin{figure}%[!ht]
-  \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/multiplot1.pdf}
-    \caption{Histogram plotted on a logarithmic scale showing the Probability of
-      surviving to at least a particualr step in different infinite square wells
-      with different boundaries $J$. The simulations were run with $10000$
-      walkers The $\lambda J^2$ values for each are shown. The values get closer
-      to the theoretical value of $\frac{\pi^2}{8} = 1.2337$ as we increase the
-      size of the well. This is likely due to more walkers surviving to a higher
-      number of steps, as the well size is increased.}
-    \label{fig:multi_line_plot}
-  \end{center}
-\end{figure}
-
 \section{Conclusions}
@@
 energies of a quantum system using Random walk computational simulations. The
-investigation focussed on an Infinite Square Well, but is easily extended to a
-Symmetric potential. The simualation was written in C++ to maximise performance
-and is available at \todo{cite}.
+investigation focussed on a one dimensional infinite square well, but can easily
+be extended to more complex systems such as a circular well in two dimensions.
 
@@
 determining the ground state energy of a quantum system, and showed that this
-method is more effective for larger wells, i.e. wells with larger
-boundaries. This is because for wells with larger boundaries, the walker can
-take a larger number of steps on average before dying, and thus can populate
-larger step bins. Thus, this method produces data that is close to the
-theoretical result for larger infinite square wells.
+method produces more accurate results for ground state energies of larger wells.
+This is because for wells with larger boundaries, the walker can take a larger
+number of steps on average before dying, and thus can populate larger step
+bins. Thus, this method produces data that is close to the theoretical result
+for larger infinite square wells.
 
@@
 \frac{\hbar^2}{mJ^2}$, where $R$ also corresponds to the boundary of the
-well. Thus, we expect our calculated result to be $\lambda R^2 = \lambda J^2 =
+well. Thus, we expect our calculated result to be $\lambda J^2 =
 \frac{\pi^2}{8}$.
@@
 
+\pagebreak
 \appendices

### 2020-04-20 Paper/main.tex
Added abstract section

@@
   In this paper, we present a novel way of calculating ground state energies for
-  a quantum simulation using a Random Walk Monte Carlo simulation.
+  a quantum simulation using a Random Walk Monte Carlo simulation. The random
+  walk consists of a walker making steps in random directions, with each step
+  having a probability of causing the walker to die and the random walk to end,
+  with the probability determined by a function of position. The function can be
+  chosen to model specific quantum systems. The rate of death of the walkers is
+  used to calculate the ground state energy.
+
+  This paper explores the efficacy of such a method in reproducing the known
+  ground state energy of an infinite square well, and the extensibility of the
+  method to more complex systems. We found that this method is very good at
+  reproducing the known results to a high precision, and with good reliability,
+  having very small variance in repeats. The method is extensible to higher
+  dimensions, with a linear increase in time-complexity for each added dimension.
 \end{abstract}

### 2020-04-20 plotcpp.py
Added extra functions and made plot fonts larger

@@ -1,9 +1,16 @@
+import matplotlib
 import numpy as np
 import matplotlib.pyplot as plt
 from scipy.optimize import curve_fit
 from subprocess import call
 import warnings
 warnings.filterwarnings("ignore")
+
+font = {'family': 'normal',
+        'weight': 'bold',
+        'size': 18}
+
+matplotlib.rc('font', **font)
 
 
 def run_model(dimen, iteration, maxSteps=0, prob=0.1, potential="", boundary=3):
@@ -47,8 +54,9 @@ def exp_plot(data, show=True, skip=0, start=1):
 
         plt.ylabel('Probability of Death')
         plt.xlabel('Time Survived (no. of steps)')
-        plt.legend()
-        # plt.savefig("./Paper/images/exp_plot.pdf")
+        plt.tight_layout()
+        plt.savefig("./Paper/images/exp_plot.pdf")
+        # plt.savefig("./Paper/images/exp_plot_cutoff.pdf")
         plt.show()
     return popt[1]
 
@@ -81,7 +89,9 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
         plt.ylabel('Probability of Survival')
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
+        plt.tight_layout()
         plt.savefig("./Paper/images/cum_exp_plot.pdf")
+        # plt.savefig("./Paper/images/cum_exp_plot_cutoff.pdf")
         plt.show()
 
     residuals = cum_y - exp_curve(x, *popt)
@@ -114,10 +124,10 @@ def line_plot(data, show=True, skip=0, start=1):
         plt.plot(x, y, marker='.', ls=' ')
         # plt.plot(x, exp_curve(x, *popt), c='r', label="Fitted Curve")
 
-        plt.ylabel('log(Probability of Death)')
+        plt.ylabel('Probability of Death')
         plt.xlabel('Time Survived (no. of steps)')
-        plt.legend()
-        # plt.savefig("./Paper/images/line_plot.pdf")
+        plt.tight_layout()
+        plt.savefig("./Paper/images/line_plot.pdf")
         plt.show()
     return popt[1]
 
@@ -135,6 +145,7 @@ def cum_line_plot(data, show=True, skip=0, start=1):
     y = hist[0][skip:]
 
     cum_y = np.cumsum(y[::-1])[::-1]
[…]

### 2020-04-20 cartoon.py
Made plot fonts larger, so they are suitable for paper

@@ -1,6 +1,13 @@
+import matplotlib
 import matplotlib.pyplot as plt
 import numpy as np
 import random
+
+font = {'family': 'normal',
+        'weight': 'bold',
+        'size': 18}
+
+matplotlib.rc('font', **font)
 
 length = 20
 x = np.linspace(0, length, length+1)
@@ -14,5 +21,6 @@ plt.rc("font", family="Serif")
 plt.plot(x, y, marker='o', markersize=20)
 plt.xlabel("Step Number")
 plt.ylabel("Position")
+plt.tight_layout()
 plt.savefig("./Paper/images/cartoon.pdf")
 plt.show()

### 2020-04-20 Paper/main.tex
Edited plot formatting and deleted unnecessary comments

@@
 \begin{abstract}
-% Provide a summary of the session. What was done, what measurements were taken,
-% brief methods, what calculations, brief conclusion.  The Abstract should be
-% approximately 250 words or fewer, italicized, in 10-point Times (or Times
-% Roman.) Please leave two spaces between the Abstract and the heading of your
-% first section.  It should briefly summarize the essence of the paper and address
-% the following areas without using specific subsection titles. Objective: Briefly
-% state the problem or issue addressed, in language accessible to a general
-% scientific audience. Technology or Method: Briefly summarize the technological
-% innovation or method used to address the problem. Results: Provide a brief
-% summary of the results and findings. Conclusions: Give brief concluding remarks
-% on your outcomes. Detailed discussion of these aspects should be provided in the
-% main body of the paper.
   In this paper, we present a novel way of calculating ground state energies for
@@
   \begin{center}
-    \includegraphics[width=0.45\textwidth]{images/multiplot1.pdf}
+    \includegraphics[width=0.45\textwidth]{images/multiplot.pdf}
     \caption{Histogram plotted on a logarithmic scale showing the Probability of

### 2020-04-20 Paper/main.tex
Made many minor changes based on feedback

@@
   chosen to model specific quantum systems. The rate of death of the walkers is
-  used to calculate the ground state energy.
-
-  This paper explores the efficacy of such a method in reproducing the known
-  ground state energy of an infinite square well, and the extensibility of the
-  method to more complex systems. We found that this method is very good at
-  reproducing the known results to a high precision, and with good reliability,
-  having very small variance in repeats. The method is extensible to higher
-  dimensions, with a linear increase in time-complexity for each added dimension.
+  used to calculate the ground state energy. This paper explores the efficacy of
+  such a method in reproducing the known ground state energy of an infinite
+  square well, and the extensibility of the method to more complex
+  systems. Using the infinite square well example, the simulation found the
+  energy proportionality to be $1.2339 \pm 0.0008$, which is consister to high
+  precision with the known $\frac{pi^2}{8}$ theoretical constant. Thus, we found
+  that this method is very good at reproducing the known results to a high
+  precision, and with good reliability, having very small variance in
+  repeats. The method is extensible to higher dimensions, with a linear increase
+  in time-complexity for each added dimension.
 \end{abstract}
@@
 \section{Introduction}
-\IEEEPARstart{T}{he} developments in computer power in recent years has opened
+\IEEEPARstart{T}{he} developments in computer power in recent years have opened
 up the possibility for novel computational solutions to many problems that were
@@
 problems and run simulations that were previously too computationally intensive
-to do.
-
-One such problem is the calculation of the ground state energies of different
-quantum systems. Many methods exist for solving these problems, using both
-classical and quantum computational approaches. Whilst generally it may be true
-that Quantum computating approahes are more suited to solving such problems
+to do.  One such problem is the calculation of the ground state energies of
+different quantum systems. Many methods exist for solving these problems, using
+both classical and quantum computational approaches. Whilst generally it may be
+true that Quantum computating approahes are more suited to solving such problems
 \cite{Mazzola}, these approaches are still in infancy and are not readily
@@
 In this investigation, we explore an alternative Monte Carlo method using Random
-Walk simulations, and demonstrate its efficacy with simple systems.
+Walk simulations, and demonstrate its efficacy with simple systems. This
+approach has applications in many areas of Quantum Physics and is values due to
+its effectiveness for more complicated systems.
 
@@
 Random walks descibe motion as a series of steps in some vector space, with the
-direction of each step being random, i.e. with there being an equal likelihood
+direction of each step being random, i.e. with there being an assigned likelihood
 of a step in each possible direction. Consider a simple 1-dimensional line and a
@@
       simulation. The average position of the walker does not necessarily remain
-      at the origin as one might naively expect. Instead it is normal for the
+      at the origin as one might expect. Instead it is normal for the
       walker to finish the walk at some distance from the origin, as shown here.}
@@
 In this example, the walker had an equal likelihood of stepping forward or
-backwards, but we can bias in one way if we want to model a particular
+backwards, but we can add a bias in a direction if we want to model a particular
 phenomenon. The walk is also easily extensible to multiple dimensions, as for
@@
 
-Let us define $p(j,n)$ as the probability that the walker will be at position
-$j$ after $n$ steps and $a(j)$ as the probability that the walker will die at
+Let us define $p(j,n+1)$ as the probability that the walker will be at position
+$j$ after $n+1$ steps and $a(j)$ as the probability that the walker will die at
 position $j$. Thus, for this to be the case, the walker would have had position
-$j\pm1$ after $n-1$ steps. Thus, we can say:
+$j\pm1$ after $n$ steps. Thus, we can say:
 
@@
 each term in this expression and obtain a differential equation. If we then
-make the ansatz substitution:
+make an ansatz substitution:
 
@@
 \end{equation}
-where $q(j)$ is an arbitrary function and $\lambda$ is the rate of death, then
-we find:
+where $q(j)$ is an arbitrary function and $\lambda$ is the rate of death, the
+differential equation in $p(j,n)$ simplifies to:
 
@@
 where J is a well-defined boundary. So the walker cannot die inside the well but
-wil immediately die when they step outside, which we expect will definitely
+wil immediately die when they step outside, which we expect will mostly
 happen given sufficient time. Inside the well, the potential is simply that of a
@@
 \begin{equation}
-  \frac{-\hbar^2}{2m}\frac{d^2 \psi}{dx^2} = E\psi(x)
+  \frac{-\hbar^2}{2m}\frac{d^2 \psi}{dj^2} = E\psi(j)
   \nonumber
@@
   E = \lambda R^2 \frac{\hbar^2}{mJ^2}
-  \nonumber
+  \label{eq:kasia}
 \end{equation}
@@
 $\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \cite{Davies1998}, so we expect to find $\lambda
-R^2$ close to $\frac{\pi}{8}$.
+R^2$ close to $\frac{\pi^2}{8}$.
 
@@
 
-We then consider the probability that a walker will survive $n$ steps, and use
+We then considered the probability that a walker will survive $n$ steps, and use
 the relationship between the number of walkers surviving $n$ steps and $n$ to
@@
 well, or if they reach this maximum number of steps, whichever happens
-first. However, this will introduce some systematic error into the simulation,
-as there will be a disproportionately high number of walkers dying on the
-maximum number of steps. We also investigated these effects here.
+first. The effect of this method on the result is investigated in this paper.
 
-We expect to see an effect on the accuracy of our final ground state depending
-on the size of the infinite well. We investigate these effects by comparing the
-calculated ground state energy to the theoretical energy for different sized wells.
+% However, this will introduce some systematic error into the simulation,
+% as there will be a disproportionately high number of walkers dying on the
+% maximum number of steps. We also investigated these effects here.
+
+% We expect to see an effect on the accuracy of our final ground state depending
+% on the size of the infinite well. We investigate these effects by comparing the
+% calculated ground state energy to the theoretical energy for different sized wells.
 
@@
   \centering
-  \subfloat[Histogram of probability of surviving to at least a particlar step]
+  \subfloat[Linear Scale]
   {\includegraphics[width=0.5\textwidth]{images/cum_exp_plot.pdf}
@@
   \centering
-  \subfloat[Histogram of probability of surviving to at least a particular step
-  in a logarithmic scale]
+  \subfloat[Log Scale]
   {\includegraphics[width=0.5\textwidth]{images/cum_line_plot.pdf}
   \label{fig:cumloghist}}
-  \caption{Histogram showing the Probability of surviving to at least a
+  \caption{Histograms showing the Probability of surviving to at least a
     particular step in an infinite square well with $J = 20$. The peak of 1 does
@@
     neglected in the plot as prior to this step the exponential shape is less
-    clear, as explained by Figure \ref{fig:hist}. An exponential decay curve
-    provides a good fit, with an $R^2$ value of 0.9999998, very close to
-    1. Plotting on a logarithmic scale shows the straight line fit, the gradient
-    of which is $\lambda$, giving $\lambda J^2 = 1.2334$, with a negligible
-    error. The fluctuation in the higher step number regions is due to the large
-    variance in the small number of walkers that die at these steps.}
+    clear. An exponential decay curve provides a good fit, with an $R^2$ value
+    of 0.9999998. Plotting on a logarithmic scale shows the straight line fit,
+    the gradient of which is $\lambda$, giving $\lambda J^2 = 1.2334$, with a
+    negligible error. The fluctuation in the higher step number regions is due
+    to the large variance in the small number of walkers that die at these
+    steps.}
   \label{fig:cumplots}
@@
 
-The simulation was first run for an infinite square well with boundary $J=20$
-with 1000000 walkers. The number of walkers surviving at each step was recorded
-and the histograms in Figure \ref{fig:cumplots} were created. The probability
+% The simulation was first run for an infinite square well with boundary $J=20$
+% with 1000000 walkers. The number of walkers surviving at each step was recorded
+% and the histograms in Figure \ref{fig:cumplots} were created. The probability
+% that a walker will survive at a particular step is simply the 1 minus the
+% normalised cumulative sum of walkers dying at each step. The curve has been
+% fitted with an exponential function of the form in Equation
+% \ref{eq:firsteq}.
+
+We first investigated an infinite square well with boundary $J=20$ and 1000000
+walkers. We found the energy constant to be $1.2339 \pm 0.0008$, calculated from
+the probability distribution of survival at a particular step. The probability
 that a walker will survive at a particular step is simply the 1 minus the
-normalised cumulative sum of walkers dying at each step. The curve has been
-fitted with an exponential function of the form in Equation
-\ref{eq:firsteq}. This results in a very good fit, with an $R^2$ value of
+normalised cumulative sum of walkers dying at each step. Figure
+\ref{fig:cumplots} presents this probability and confirms the Anstatz of the
+exponential function. The curve has been fitted with an exponential function of
+the form in Equation \ref{eq:firsteq}. The gradient of Figure
+\ref{fig:cumloghist} allowed for calculation of death rate which from Equation
+\ref{eq:kasia} gives the calculated energy.
+
+Figure \ref{fig:cumplots} results in a very good fit, with an $R^2$ value of
 0.9999998, indicating the data does not vary much from the curve of best
 fit. This is likely due to the very large number of walkers used in this
-experiment, as allowed by the performant C++ implementation.
-
-We can see this better in Figure \ref{fig:cumloghist}, which is the same
-exponential plot fitted on a logarithmic scale. The closeness of the data to the
-line of best fit is evident here. The error in the fitted parameters is
-negligible, as shown by the $R^2$ value. The gradient of the fitted line is
-taken to be $\lambda$ and thus allows us to calculate $\lambda J^2 = 1.2334$,
-compared to the theoretical value of $\frac{\pi^2}{8} = 1.2337$, quoting both
-values to the precision at which they vary. Since the numerical error in the
-fits is negligible, it cannot be propagated into an error in the final
-answer. Thus, we get the error in the final answer from repeated runs of the
-simulation and taking the standard deviation of the many values.
+experiment, as allowed by the performant C++ implementation.  We can see this
+better in Figure \ref{fig:cumloghist}, which is the same exponential plot fitted
+on a logarithmic scale. The closeness of the data to the line of best fit is
+evident here. The error in the fitted parameters is negligible, as shown by the
+$R^2$ value. The gradient of the fitted line is taken to be $\lambda$ and thus
+allows us to calculate $\lambda J^2 = 1.2334$, compared to the theoretical value
+of $\frac{\pi^2}{8} = 1.2337$, quoting both values to the precision at which
+they vary. Since the numerical error in the fits is negligible, it cannot be
+propagated into an error in the final answer. Thus, we get the error in the
+final answer from repeated runs of the simulation and taking the standard
+deviation of the many values.
 
@@
     \caption{The probability of dying on a particular step in an infnite square
-      well with $J=20$, plotted on a logarithmic scale. As explained for Figure
-      \ref{fig:hist}, the peak probability is on a step greater than $J$. This
-      is clear in this plot. It is also evident that there is significantly more
-      spread in the points at higher steps. This is due to there being
-      significantly fewer walkers dying on these steps, so the relative
-      differences are higher. This explains the fluctuations seen at higher
-      steps in Figure \ref{fig:cumloghist}.}
+      well with $J=20$ as in Figure \ref{fig:hist}, plotted on a logarithmic
+      scale. As explained for Figure \ref{fig:hist}, the peak probability is on
+      a step greater than $J$. This is clear in this plot. It is also evident
+      that there is significantly more spread in the points at higher
+      steps. This is due to there being significantly fewer walkers dying on
+      these steps, so the relative differences are higher. This explains the
+      fluctuations seen at higher steps in Figure \ref{fig:cumloghist}.}
     \label{fig:loghist}
@@
 can observe this in Figure \ref{fig:loghist}. At higher step numbers, the spread
-is clearly larger due to the greater relative variance in the small number of
-walkers surviving to this many steps. When this data is cumulatively summed to
-calculate the probability of survival shown in Figure \ref{fig:cumloghist}, the
-spread is present as the fluctuations.
+is significantly larger due to the greater relative variance in the small number
+of walkers surviving to this many steps. When this data is cumulatively summed
+to calculate the probability of survival shown in Figure \ref{fig:cumloghist},
+the spread is present as the fluctuations.
 
@@
   \centering
-  \subfloat[Probability of dying on a particlar step with a step cutoff]
+  \subfloat[Probability of dying on a particlar step in Linear scale]
   {\includegraphics[width=0.5\textwidth]{images/exp_plot_cutoff.pdf}
@@
   \subfloat[Probability of surviving to at least a particular step in a
-  logarithmic scale with a step cutoff]
+  logarithmic scale]
   {\includegraphics[width=0.5\textwidth]{images/cum_line_plot_cutoff.pdf}
@@
   disproportionately high number of walkers dying at this maximum number, 2000
-  in this case, as shown by Figure \ref{fig:expcutoff}. However, this results in
+  in this case, as shown by Figure \ref{fig:expcutoff}. Although this presents
   no fluctuation at higher number of steps, as shown in Figure
-  \ref{fig:cum_line_cutoff_plot}, though some systematic error is introduced
+  \ref{fig:cum_line_cutoff_plot}, some systematic error is introduced
   through this method.}
@@
 such high variance in the number of walkers surviving to high number of
-steps. This is presented in Figure \ref{fig:cum_line_cutoff_plot}. While this
-fit is observed to be better, with a higher $R^2$ value, some systematic error
-has been introduced since there will now be a disproportionately high number of
-walkers dying at the cutoff step as can be seen in Figure
-\ref{fig:expcutoff}. Thus, the final $\lambda J^2$ value will be less
-accurate. On a faster computer, with more efficient code, it is possible to
-forgo the step cutoff and allow the simulation to run until all the walkers
-die. This may take much longer but will ensure there will not be such a
+steps. This is presented in Figure \ref{fig:cum_line_cutoff_plot}. While the
+Figure \ref{fig:cum_line_cutoff_plot} fit is observed to be better, with a
+higher $R^2$ value, some systematic error has been introduced since there will
+now be a disproportionately high number of walkers dying at the cutoff step as
+can be seen in Figure \ref{fig:expcutoff}. Thus, the final $\lambda J^2$ value
+will be less accurate. On a faster computer, with more efficient code, it is
+possible to forgo the step cutoff and allow the simulation to run until all the
+walkers die. This may take much longer but will ensure there will not be such a
 systematic error introduced. This is the method used in this investigation.
@@
 accuracy of the final answer. Figure \ref{fig:multi_line_plot} presents the
-cumulative summed histograms with their fitted lines for many different boundary
+probability plot from Figure \ref{fig:cumloghist} for many different boundary
 $J$ values. No step cutoff was introduced. The calculated $\lambda J^2$ value is
-shown in the legend. As shown, the gradient changes, but this is to be expected
-since the expected highest number of steps would increase as the boundary is
-larger, since there is more space for the walker to move before reaching a
-boundary. As shown in the legend, the calculated $\lambda J^2$ values get closer
-and closer and closer to the theoretical value as $J$ increases. This is due to
-the fact that as $J$ increases, there are more walkers surviving to larger
-number of steps. Thus, we can say that using a larger value of $J$ will result
-in a more accurate answer but will also be more computationally intensive and
-take longer. Thus, we make a tradeoff between speed and accuracy and choose
-$J=20$ for the final investigation.
+shown in the legend. The gradient evidently changes, since the expected highest
+number of steps would increase as the boundary is larger, as there is more
+space for the walker to move before reaching a boundary. As shown in the legend,
+the calculated $\lambda J^2$ values get closer and closer to the
+theoretical value as $J$ increases. This is due to the fact that as $J$
+increases, there are more walkers surviving to larger number of steps. Thus, we
+can say that using a larger value of $J$ will result in a more accurate answer
+but will also be more computationally intensive and take longer. Thus, we make a
+tradeoff between speed and accuracy and choose $J=20$ for the final
+investigation.
 
@@
 investigation focussed on a one dimensional infinite square well, but can easily
-be extended to more complex systems such as a circular well in two dimensions.
+be extended to more complex systems such as a cirular well in two dimensions.
 
@@
 determining the ground state energy of a quantum system, and showed that this
-method produces more accurate results for ground state energies of larger wells.
-This is because for wells with larger boundaries, the walker can take a larger
-number of steps on average before dying, and thus can populate larger step
-bins. Thus, this method produces data that is close to the theoretical result
-for larger infinite square wells.
+Monte Carlo method produces more accurate results for ground state energies of
+larger wells.  This is because for wells with larger boundaries, the walker can
+take a larger number of steps on average before dying, and thus can populate
+larger step bins. Thus, this method produces data that is close to the
+theoretical result for larger infinite square wells.
 
-The general theoretical result for the ground state energy of an infinite square
-well is $\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ where $J$ is the boundary of the
-well, and this method allows for the calculation of $\lambda R^2
-\frac{\hbar^2}{mJ^2}$, where $R$ also corresponds to the boundary of the
-well. Thus, we expect our calculated result to be $\lambda J^2 =
-\frac{\pi^2}{8}$.
-
-This method provided $\lambda J^2 = 1.2339 \pm 0.0008$, which lies within the
-range of the theoretical result.
+The numerical result found the ground state energy proportionality constant to
+be $\lambda J^2 = 1.2339 \pm 0.0008$, which is consistent with the known
+theoretical value of $\frac{\pi^2}{8}$.
 

### 2020-04-20 lattice.cpp
Added provisions for circular wells

@@ -72,6 +72,12 @@ public:
 		}
 	}
 
+	void addPosition(vector<int> pos){
+		for(int i=0; i<coordinates.size(); i++){
+			pos.push_back(coordinates[i]);
+		}
+	}
+
 	// resets lattice to start position
 	void reset(int d){
 		vector<int> coordinates_new;
@@ -182,6 +188,7 @@ int main(int argc, char* argv[]){
 
 	
 	vector<int> data;
+	vector<int> positions;
 
 	// run the random walk
 	for(int i=0; i<iterations; i++){
@@ -196,6 +203,12 @@ int main(int argc, char* argv[]){
 			caught = lattice.caught(probability, potential, boundary, maxSteps);
 		}
 		// append to data
+
+		if(potential == "circle"){
+			for(int i=0; i<lattice.coordinates.size(); i++){
+				positions.push_back(lattice.coordinates[i]);
+			}
+		}
 		data.push_back(time);
 	}
 
@@ -205,5 +218,13 @@ int main(int argc, char* argv[]){
 		myfile << data[i] << "\n";
 	}
 	myfile.close();
+
+	ofstream myfile1;
+	myfile1.open("positions.dat");
+	for(int i=0; i<positions.size(); i++){
+		myfile1 << positions[i] << "\n";
+	}
+	myfile1.close();
+	
 	return 0;
 }

### 2020-04-20 plotcpp.py

@@ -47,7 +47,7 @@ def exp_plot(data, show=True, skip=0, start=1):
     x = hist[1][skip:-1]
     y = hist[0][skip:]
 
-    popt, _ = curve_fit(exp_curve, x, y)
+    # popt, _ = curve_fit(exp_curve, x, y)
 
     if show:
         # plt.plot(x, exp_curve(x, *popt), c='r', label="Fitted Curve")
@@ -55,10 +55,9 @@ def exp_plot(data, show=True, skip=0, start=1):
         plt.ylabel('Probability of Death')
         plt.xlabel('Time Survived (no. of steps)')
         plt.tight_layout()
-        plt.savefig("./Paper/images/exp_plot.pdf")
+        # plt.savefig("./Paper/images/exp_plot.pdf")
         # plt.savefig("./Paper/images/exp_plot_cutoff.pdf")
         plt.show()
-    return popt[1]
 
 
 def cum_exp_plot(data, show=True, skip=0, start=1):
@@ -90,7 +89,7 @@ def cum_exp_plot(data, show=True, skip=0, start=1):
         plt.xlabel('Time Survived (no. of steps)')
         plt.legend()
         plt.tight_layout()
-        plt.savefig("./Paper/images/cum_exp_plot.pdf")
+        # plt.savefig("./Paper/images/cum_exp_plot.pdf")
         # plt.savefig("./Paper/images/cum_exp_plot_cutoff.pdf")
         plt.show()
 
@@ -117,7 +116,7 @@ def line_plot(data, show=True, skip=0, start=1):
     x = hist[1][skip:-1]
     y = hist[0][skip:]
 
-    popt, _ = curve_fit(exp_curve, x, y)
+    # popt, _ = curve_fit(exp_curve, x, y)
 
     if show:
         plt.yscale("log")
@@ -127,9 +126,8 @@ def line_plot(data, show=True, skip=0, start=1):
         plt.ylabel('Probability of Death')
         plt.xlabel('Time Survived (no. of steps)')
         plt.tight_layout()
-        plt.savefig("./Paper/images/line_plot.pdf")
+        # plt.savefig("./Paper/images/line_plot.pdf")
         plt.show()
-    return popt[1]
 
 
 def cum_line_plot(data, show=True, skip=0, start=1):
@@ -158,7 +156,7 @@ def cum_line_plot(data, show=True, skip=0, start=1):
         plt.xlabel('Time Survived (no. of steps)')
[…]

### 2020-04-20 plotcpp.py
modified starting parameters

@@ -281,10 +281,10 @@ def spatial_plot(data, dimen, show=True, bins=100):
 
 if __name__ == "__main__":
 
-    dimen = 2
+    dimen = 1
     iteration = 1000000
     maxSteps = 0
-    potential = "circle"
+    potential = "square"
     boundary = 20
     prob = 0.1
 

### 2020-04-20 Paper/main.tex
Spell-check and grammar corrections

@@
   systems. Using the infinite square well example, the simulation found the
-  energy proportionality to be $1.2339 \pm 0.0008$, which is consister to high
-  precision with the known $\frac{pi^2}{8}$ theoretical constant. Thus, we found
+  energy proportionality to be $1.2339 \pm 0.0008$, which is consistent to high
+  precision with the known $\frac{\pi^2}{8}$ theoretical constant. Thus, we found
   that this method is very good at reproducing the known results to a high
@@
 both classical and quantum computational approaches. Whilst generally it may be
-true that Quantum computating approahes are more suited to solving such problems
+true that Quantum computing approaches are more suited to solving such problems
 \cite{Mazzola}, these approaches are still in infancy and are not readily
 accessible. Thus, there exist an abundance of classical computing approaches,
-such as the Variational-Relaxiation algorithm \cite{Schroeder2017}. This is a
+such as the Variational-Relaxation algorithm \cite{Schroeder2017}. This is a
 particularly useful algorithm for two-dimensional systems with non-separable
@@
 
-Random walks descibe motion as a series of steps in some vector space, with the
+Random walks describe motion as a series of steps in some vector space, with the
 direction of each step being random, i.e. with there being an assigned likelihood
@@
 where J is a well-defined boundary. So the walker cannot die inside the well but
-wil immediately die when they step outside, which we expect will mostly
+will immediately die when they step outside, which we expect will mostly
 happen given sufficient time. Inside the well, the potential is simply that of a
@@
 $\lambda$, we can calculate the ground state energy of the infinite square
-well. The known ground state energy of an infnite square well is
+well. The known ground state energy of an infinite square well is
 $\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \cite{Davies1998}, so we expect to find $\lambda
@@
 normalised cumulative sum of walkers dying at each step. Figure
-\ref{fig:cumplots} presents this probability and confirms the Anstatz of the
+\ref{fig:cumplots} presents this probability and confirms the ansatz of the
 exponential function. The curve has been fitted with an exponential function of
@@
   greater than but still close to $J$ since it would require walking in the same
-  direction a dispropotionate number of times.
+  direction a disproportionate number of times.
 \end{itemize}
@@
     \includegraphics[width=0.45\textwidth]{images/exp_plot.pdf}
-    \caption{The probability of dying on a particular step in an infnite square
+    \caption{The probability of dying on a particular step in an infinite square
       well with $J=20$. As can be seen, the peak is away from the origin. This
@@
     \includegraphics[width=0.45\textwidth]{images/line_plot.pdf}
-    \caption{The probability of dying on a particular step in an infnite square
+    \caption{The probability of dying on a particular step in an infinite square
       well with $J=20$ as in Figure \ref{fig:hist}, plotted on a logarithmic
@@
   \label{fig:cum_line_cutoff_plot}}
-  \caption{Histograms showing the results of the simulation when a maximm number
+  \caption{Histograms showing the results of the simulation when a maximum number
   of steps is introduced. If a walker reaches this number of steps, they
@@
 but will also be more computationally intensive and take longer. Thus, we make a
-tradeoff between speed and accuracy and choose $J=20$ for the final
+trade-off between speed and accuracy and choose $J=20$ for the final
 investigation.
@@
 investigation focussed on a one dimensional infinite square well, but can easily
-be extended to more complex systems such as a cirular well in two dimensions.
+be extended to more complex systems such as a circular well in two dimensions.
 
@@
 walker. Let us denote the probability that the walker is at position $j$ after
-$n$ steps as $p(j,n)$ and the probabilty that the walker will die at position
+$n$ steps as $p(j,n)$ and the probability that the walker will die at position
 $j$ as $a(j)$. We will denote the position-step number coordinates as $[j,
